### 2013-09-25 nothing_to_hide/presentation.tex
Added initial shell.

\documentclass{beamer}
\usepackage{graphicx}

\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\newcommand{\ts}{\textsuperscript}

\usetheme{Boadilla}

% items enclosed in square brackets are optional; explanation below
\title[Privacy in Art, Books, and Film]{I've Got Nothing to Hide: \\
  Exploring Privacy in Art, Books, and Film}
\author[Josh Datko]{Joshua Datko}
\institute[Drexel]{
  Department of Computer Science\\
  Drexel University\\
  Philadelphia, PA 19103\\[1ex]
  %\texttt{jbd65@drexel.edu}
}
\date[September 2013]{September 28, 2013}

\setbeamertemplate{bibliography item}[text]

\begin{document}

%--- the titlepage frame -------------------------%
\begin{frame}[plain]
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{Motivation}

  \begin{itemize}
  \item Tor runs on volunteers.
  \item Tor needs more volunteers.
  \item Tor should incentivize relay and bridge operators.
  \end{itemize}

  \begin{block}{People like money.}
    Provide incentives for Tor server operators through Bitcoin.
  \end{block}
\end{frame}

% \begin{frame}
% \frametitle{Survival Curve}
%   \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{survival}
% \end{frame}
%% \begin{frame}
%%   \frametitle{Bitcoin}

%%   Bitcoin is a peer-to-peer electronic currency based on
%%   proof-of-work. \cite{nakamoto2009bitcoin}

%%   \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{bitcoin_volume}

%% \end{frame}

%% \begin{frame}
%%   \frametitle{Can Bitcoin provide incentives?}

%%   Bitcoin is not
%%   anonymous.\cite{journals/iacr/AndroulakiKRSC12} \cite{journals/corr/abs-1107-4524}

%%   Combining Bitcoin as is with Tor would expose Tor users.  We seek to
%%   investigate alternative means of payments.
%%   \begin{itemize}
%%   \item Tor client joins a Bitcoin mining pool and payment goes
%%     directly to the Tor Server?
%%   \item Can we use Zerocoin? \cite{Miers:2013:ZAD:2497621.2498124}
%%     \end{itemize}

%%   \begin{block}{Anonymity}
%%     Tor incentives can't compromise anonymity!!
%%   \end{block}
%% \end{frame}

%% \begin{frame}
%%   \frametitle{Approach}

%%   \begin{itemize}
%%   \item Compare BitTor to other incentive
%%     systems.\cite{Jansen:2010:RNT:1866307.1866344}\cite{lira-ndss13}\cite{raykova-pet2008}
%%   \item Investigate Bitcoin payment methods.
%%   \item Provide anonymity analysis.
%%     \item Prototype BitTor and investigate performance

%%     \end{itemize}

%%   \begin{block}{Live and dynamic systems}
%%     Bitcoin = money, Tor = privacy $\rightarrow$ testing to be done ``offline.''
%%   \end{block}
%% \end{frame}

%% \begin{frame}[allowframebreaks]

%%   \frametitle{References}
%%   \begin{small}
%%   \phantomsection
%%   \addcontentsline{toc}{section}{\bibname}
%%   \bibliographystyle{acm}
%%   \bibliography{bitcoin,tor}
%%   \end{small}

%% \end{frame}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2013-09-25 nothing_to_hide/presentation.tex
Added the neighbors project

@@
   Philadelphia, PA 19103\\[1ex]
-  %\texttt{jbd65@drexel.edu}
+  \texttt{jbd65@drexel.edu}
 }
@@
   \end{block}
+\end{frame}
+
+\begin{frame}
+
+\frametitle{\emph{The Neighbors} by Arne Svenson}
+
+\begin{itemize}
+\item Photographer takes pictures of his neighbors, without their
+  knowledge,  in Tribeca (NYC).
+\item Two neighbors sued.  Their children were in the photos.
+\item Court ruled the artist was protected under the First Amendment.
+
+\end{itemize}
+
+\begin{block}{I have nothing to hide.}
+    Unless you take a picture of me and call it art!
+  \end{block}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{\emph{Neighbors}}
+
+    \begin{columns}[c] % the "c" option specifies center vertical alignment
+    \column{.5\textwidth} % column designated by a command
+    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{img/10_website_IMG_4763}
+
+    \column{.5\textwidth}
+    \begin{figure}
+    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{img/4_website_IMG_3013.jpg}
+    \caption{Photos Copyright Arne Svenson}
+    \end{figure}
+
+    \end{columns}
+
+\end{frame}
+
+\begin{frame}
+
+\frametitle{\emph{Bleeding Edge} by Thomas Pynchon}
+
+\begin{itemize}
+\item Released last week
+\item Very Pynchon.  Avant-garde literature ala \emph{Gravity's
+  Rainbow}
+\item Set in early 2001 in NYC.  In the post tech bust but before
+  9/11.
+\item Explores the idea of getting ``lost'' on the Internet and how
+  that ended with 9/11.
+\end{itemize}
 \end{frame}

### 2013-09-26 nothing_to_hide/presentation.tex
update.
Added little brother and art project

@@
 
-\frametitle{\emph{The Neighbors} by Arne Svenson}
+\frametitle{\emph{The Neighbors} (2013) by Arne Svenson}
 
@@
 
+\begin{frame}
+\frametitle{Face to Facebook}
+
+Stealing 1 million Facebook profiles, filtering them with face-recognition software, and then,
+posting them on a custom-made dating website, sorted by their facial
+expressions characteristics.
+
+\begin{columns}[c] % the "c" option specifies center vertical alignment
+    \column{.5\textwidth} % column designated by a command
+    \begin{itemize}
+    \item All ``singles'' were involuntarily added to a fake an
+      experimental dating site.
+    \item Let's watch the introduction video.
+    \item Great example of \emph{secondary usage}
+
+    \end{itemize}
+
+    \column{.5\textwidth}
+    \begin{figure}
+    \includegraphics[width=\textwidth,height=0.4\textheight,keepaspectratio]{img/fbFaces}
+    \caption{Facebook Faces by Joern Roeder and Jonathan Pirnay,
+      University of Visual Arts and Design Kassel, Germany, 2011}
+
+    \end{figure}
+
+    \end{columns}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{\emph{The Trial} by Franz Kafka}
+
+\begin{itemize}
+\item Referred to by the author as an example that ``depicts a
+  bureaucracy with insrutable purposes that uses people's information
+  to make important decisions about them, yet denies the people the
+  ability to participate in how their information is used.''
+
+\item Reading from beginning of \emph{The Trial}.
+\item Reading from \emph{Harper's}, September 2013, \emph{Life as a
+  Terrorist: Uncovering my FBI File} by William T. Vollmann
+\end{itemize}
+
+\begin{block}{I have nothing to hide.}
+    But when the government hides information about you, it enables a
+    sense of frustration and powerlessness.
+  \end{block}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{\emph{Little Brother} and \emph{Homeland} by Cory
+  Doctorow}
+
+\begin{columns}[c] % the "c" option specifies center vertical alignment
+    \column{.5\textwidth} % column designated by a command
+    \begin{itemize}
+    \item Cory Doctorow: EFF, Boing Boing, several books.
+    \item The day after tomorrow setting: terrorist attack San Francisco.
+    \item \emph{Little Brother} teaches you how to have a GPG Signing
+      party and how to run anonymizing software (like Tails and Tor).
+    \item Afterwards by Bruce Schneier, Andrew Huang, Jacob Appelbaum,
+      Aaron Schwartz.
+    \item \emph{Little Brother} has an \emph{excellent} Bibliography for
+      other readings on security.
+    \end{itemize}
+
+    \column{.5\textwidth}
+    \begin{figure}
+    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{img/Little-Brother}
+
+    \end{figure}
+
+    \end{columns}
+
+\end{frame}
 \begin{frame}

### 2013-09-27 nothing_to_hide/presentation.tex
Working on beginning summary.

@@
 \begin{frame}
-  \frametitle{Motivation}
+  \frametitle{I've Got Nothing to Hide}
+
+A brief summary of \emph{``I've Got Nothing to Hide'' and Other
+  Misunderstandings of Privacy} by Daniel J. Solove.
 
 \begin{itemize}
-  \item Tor runs on volunteers.
-  \item Tor needs more volunteers.
-  \item Tor should incentivize relay and bridge operators.
+\item If you have nothing to hide, what do you have to fear?
+\item More like, ``I don't care what happens, so long as it doesn't
+  happen to me.''
+\item Strongest argument has a utilitarian perspective: national
+  security is more important than my privacy.
+
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+
+\frametitle{Privacy is hard to define}
+
+The taxonomy of privacy:
+
+\begin{columns}[c] % the "c" option specifies center vertical alignment
+    \column{.5\textwidth} % column designated by a command
+
+    \begin{itemize}
+    \item Information Collection
+      \begin{itemize}
+      \item Surveillance
+      \item Interrogation
+      \end{itemize}
+    \item Information Processing
+      \begin{itemize}
+      \item Aggregation
+      \item Identification
+      \item Insecurity
+      \item Secondary Use
+      \item Exclusion
       \end{itemize}
 
-  \begin{block}{People like money.}
-    Provide incentives for Tor server operators through Bitcoin.
+    \end{itemize}
+
+    \column{.5\textwidth}
+
+    \begin{itemize}
+    \item Information Dissemination
+      \begin{itemize}
+      \item Breach of Confidentiality
+      \item Disclosure
+      \item Exposure
+      \item Increased Accessibility
+      \item Blackmail
+      \item Appropriation
+      \item Distortion
+        \end{itemize}
+    \item Invasion
+      \begin{itemize}
+      \item Intrusion
+      \item Decisional Interference
+
+        \end{itemize}
+
+      \end{itemize}
+
+    \end{columns}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{columns}[c] % the "c" option specifies center vertical alignment
+    \column{.5\textwidth} % column designated by a command
+
+    \begin{block}{}
+      Privacy in Art.
     \end{block}
+
+    \column{.5\textwidth}
+
+    \end{columns}
+
 \end{frame}
@@
 \begin{frame}
+
+\begin{columns}[c] % the "c" option specifies center vertical alignment
+    \column{.5\textwidth} % column designated by a command
+
+    \begin{block}{}
+      Privacy in Fiction.
+    \end{block}
+
+    \column{.5\textwidth}
+
+    \end{columns}
+
+\end{frame}
+
+\begin{frame}
 \frametitle{\emph{The Trial} by Franz Kafka}
@@
 \end{frame}
+
 \begin{frame}
 
-\frametitle{\emph{Bleeding Edge} by Thomas Pynchon}
+\begin{columns}[c] % the "c" option specifies center vertical alignment
+    \column{.5\textwidth} % column designated by a command
+
+    \begin{block}{}
+      Privacy in Film.
+    \end{block}
+
+    \column{.5\textwidth}
+
+    \end{columns}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{\emph{V for Vendetta} 2005}
+
+\begin{columns}[c] % the "c" option specifies center vertical alignment
+    \column{.5\textwidth} % column designated by a command
+    \begin{itemize}
+
+      \item Orwellian: state surveillance, mandatory curfews, state media.
+      \item Popularized Guy Fawkes Masks.
+      \item Banned books, art, and subversive material.
+    \end{itemize}
+
+    \includegraphics[width=\textwidth,height=0.6\textheight,keepaspectratio]{img/guy_fawkes}
+
+    \column{.5\textwidth}
+    \begin{figure}
+    \includegraphics[width=\textwidth,height=0.6\textheight,keepaspectratio]{img/banned_books}
+    %\caption{Me reading a banned book.  I would not do well in a
+      %\emph{V for Vendetta} world.}
+    \begin{block}{Caught with a banned book}
+      I would not do well in a \emph{V for Vendetta} world.
+    \end{block}
+    \end{figure}
+
+    \end{columns}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{\emph{Das Leben der Anderen} (2006)}
+\begin{columns}[c] % the "c" option specifies center vertical alignment
+    \column{.5\textwidth} % column designated by a command
+    \begin{itemize}
+
+      \item 1950 - 1990 during the DDR, a \emph{real} surveillance
+        state existed.
+      \item Nearly every item on the taxonomy of privacy is violated.
+      \item Stasi infiltration ran deep: industry, schools, and spouses.
+    \end{itemize}
+
+    \column{.5\textwidth}
+    \begin{figure}
+    \includegraphics[width=\textwidth,height=0.6\textheight,keepaspectratio]{img/stasi}
+    %\caption{Me reading a banned book.  I would not do well in a
+      %\emph{V for Vendetta} world.}
+
+    \end{figure}
+
+    \end{columns}
+
+\begin{block}{Why invent dystopias?}
+      History serves as a better example.
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Discussion Ideas}
 
 \begin{itemize}
-\item Released last week
-\item Very Pynchon.  Avant-garde literature ala \emph{Gravity's
-  Rainbow}
-\item Set in early 2001 in NYC.  In the post tech bust but before
-  9/11.
-\item Explores the idea of getting ``lost'' on the Internet and how
-  that ended with 9/11.
+\item Would you keep your blinds open in NYC if you lived there?  What
+  if your neighbor was taking pictures?
+\item When, if ever, would you consider filling a Freedom of
+  Information Act (FOIA) request for your file?
+\item The TSA back-scatter machines have raised privacy concerns
+  because of the revealing images.  Would you / did you go throw them?
+  Did you feel any pressure to choose the scanner over the pat-down?
+
 \end{itemize}
+
 \end{frame}
-
-% \begin{frame}
-% \frametitle{Survival Curve}
-%   \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{survival}
-% \end{frame}
-%% \begin{frame}
-%%   \frametitle{Bitcoin}
-
-%%   Bitcoin is a peer-to-peer electronic currency based on
-%%   proof-of-work. \cite{nakamoto2009bitcoin}
-
-%%   \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{bitcoin_volume}
-
-%% \end{frame}
-
-%% \begin{frame}
-%%   \frametitle{Can Bitcoin provide incentives?}
-
-%%   Bitcoin is not
-%%   anonymous.\cite{journals/iacr/AndroulakiKRSC12} \cite{journals/corr/abs-1107-4524}
-
-%%   Combining Bitcoin as is with Tor would expose Tor users.  We seek to
-%%   investigate alternative means of payments.
-%%   \begin{itemize}
-%%   \item Tor client joins a Bitcoin mining pool and payment goes
-%%     directly to the Tor Server?
-%%   \item Can we use Zerocoin? \cite{Miers:2013:ZAD:2497621.2498124}
-%%     \end{itemize}
-
-%%   \begin{block}{Anonymity}
-%%     Tor incentives can't compromise anonymity!!
-%%   \end{block}
-%% \end{frame}
-
-%% \begin{frame}
-%%   \frametitle{Approach}
-
-%%   \begin{itemize}
-%%   \item Compare BitTor to other incentive
-%%     systems.\cite{Jansen:2010:RNT:1866307.1866344}\cite{lira-ndss13}\cite{raykova-pet2008}
-%%   \item Investigate Bitcoin payment methods.
-%%   \item Provide anonymity analysis.
-%%     \item Prototype BitTor and investigate performance
-
-%%     \end{itemize}
-
-%%   \begin{block}{Live and dynamic systems}
-%%     Bitcoin = money, Tor = privacy $\rightarrow$ testing to be done ``offline.''
-%%   \end{block}
-%% \end{frame}
-
-%% \begin{frame}[allowframebreaks]
-
-%%   \frametitle{References}
-%%   \begin{small}
-%%   \phantomsection
-%%   \addcontentsline{toc}{section}{\bibname}
-%%   \bibliographystyle{acm}
-%%   \bibliography{bitcoin,tor}
-%%   \end{small}
-
-%% \end{frame}
 

### 2013-09-27 nothing_to_hide/presentation.tex
First draft.

@@
 % items enclosed in square brackets are optional; explanation below
-\title[Privacy in Art, Books, and Film]{I've Got Nothing to Hide: \\
-  Exploring Privacy in Art, Books, and Film}
+\title[Privacy in Art, Fiction, and Film]{I've Got Nothing to Hide: \\
+  Exploring Privacy in Art, Fiction, and Film}
 \author[Josh Datko]{Joshua Datko}
@@
 \end{frame}
+
+\AtBeginSection[]
+{
+  \begin{frame}{Table of Contents}
+    \tableofcontents[currentsection]
+  \end{frame}
+
+}
+\section{Article Summary}
 
@@
 \begin{frame}
-
-\begin{columns}[c] % the "c" option specifies center vertical alignment
-    \column{.5\textwidth} % column designated by a command
-
-    \begin{block}{}
-      Privacy in Art.
-    \end{block}
-
-    \column{.5\textwidth}
-
-    \end{columns}
+\frametitle{A Tale of Two Dystopias}
+\begin{itemize}
+\item Orwellian
+  \begin{itemize}
+  \item Surveillance state.
+  \item Social control through over presence.
+  \end{itemize}
+\item Kafkaesque
+  \begin{itemize}
+  \item Information processing affects the power relationship.
+  \item Frustrate individuals and creates helplessness and powerlessness.
+  \end{itemize}
+\end{itemize}
 
 \end{frame}
+
+\begin{frame}
+\frametitle{The problem with the argument}
+
+The argument is built on the ``premise that privacy is about hiding a
+wrong'' (Bruce Schneier).
+
+\begin{itemize}
+\item No Fourth Amendment protection to data stored by third parties.
+\item Causes a chilling effect on Free Speech and Free Association.
+\item Secondary Use: Unintended use of the collected data.
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Final Point}
+
+The issue, however, often is not whether the NSA or other government
+agencies should be allowed to engage in particular forms of information
+gathering; rather, it is what kinds of oversight and accountability we
+want in place when the government engages in searches and seizures.
+
+\end{frame}
+
+\section{Privacy in Art}
+
+%% \begin{frame}
+
+%% \begin{columns}[c] % the "c" option specifies center vertical alignment
+%%     \column{.5\textwidth} % column designated by a command
+
+%%     \begin{block}{}
+%%       Privacy in Art.
+%%     \end{block}
+
+%%     \column{.5\textwidth}
+
+%%     \end{columns}
+
+%% \end{frame}
 
@@
 
-\begin{frame}
+\section{Privacy in Fiction}
 
-\begin{columns}[c] % the "c" option specifies center vertical alignment
-    \column{.5\textwidth} % column designated by a command
+%% \begin{frame}
 
-    \begin{block}{}
-      Privacy in Fiction.
-    \end{block}
+%% \begin{columns}[c] % the "c" option specifies center vertical alignment
+%%     \column{.5\textwidth} % column designated by a command
 
-    \column{.5\textwidth}
+%%     \begin{block}{}
+%%       Privacy in Fiction.
+%%     \end{block}
 
-    \end{columns}
+%%     \column{.5\textwidth}
 
-\end{frame}
+%%     \end{columns}
+
+%% \end{frame}
 
@@
 
-\begin{frame}
+\section{Privacy in Film}
 
-\begin{columns}[c] % the "c" option specifies center vertical alignment
-    \column{.5\textwidth} % column designated by a command
+%% \begin{frame}
 
-    \begin{block}{}
-      Privacy in Film.
-    \end{block}
+%% \begin{columns}[c] % the "c" option specifies center vertical alignment
+%%     \column{.5\textwidth} % column designated by a command
 
-    \column{.5\textwidth}
+%%     \begin{block}{}
+%%       Privacy in Film.
+%%     \end{block}
 
-    \end{columns}
+%%     \column{.5\textwidth}
 
-\end{frame}
+%%     \end{columns}
+
+%% \end{frame}
 
@@
 
+\section{Discussion Ideas}
+
 \begin{frame}

### 2013-09-27 nothing_to_hide/presentation.tex
Reviewer's comments.

@@
   \item Surveillance state.
-  \item Social control through over presence.
+  \item Social control through overt presence.
   \end{itemize}
@@
 \begin{frame}
-\frametitle{The problem with the argument}
+\frametitle{The problem with ``I have nothing to hide''}
 
@@
 
-The issue, however, often is not whether the NSA or other government
+``The issue, however, often is not whether the NSA or other government
 agencies should be allowed to engage in particular forms of information
 gathering; rather, it is what kinds of oversight and accountability we
-want in place when the government engages in searches and seizures.
+want in place when the government engages in searches and seizures.''
 
@@
 \begin{frame}
-\frametitle{\emph{V for Vendetta} 2005}
+\frametitle{\emph{V for Vendetta} (2005)}
 
@@
   if your neighbor was taking pictures?
-\item When, if ever, would you consider filling a Freedom of
+\item When, if ever, would you consider filing a Freedom of
   Information Act (FOIA) request for your file?

### 2013-10-21 proposal/proposal.tex
Added submitted proposal.

%File: focus_paper.tex
\documentclass[letterpaper]{article}

% Required Packages
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\usepackage{url}

\begin{document}

%%%%%%%%%%
% Pdfinfo for PDFTEX
% Uncomment and complete the following for metadata if % your paper is
% typeset using PDFTEX
\pdfinfo{
/Title (The Feasibility of Stylometry as a Service)
/Author (Josh Datko and Joseph Heenan)
/Subject (The Feasibility of Stylometry as a Service)
/Keywords (privacy anonymity stylometry )
}
%%%%%%%%%%
% Section Numbers
% Uncomment if you want to use section numbers
% and change the 0 to a 1 or 2
\setcounter{secnumdepth}{1}
%%%%%%%%%%
% Title, Author, and Address Information
\title{The Feasibility of Stylometry as a Service}
\author{Josh Datko \and Joseph Heenan\\ Drexel University\\
CS680: Privacy in the Electronic Society\\
}
%%%%%%%%%%
% Body of Paper Begins \begin{document}
\maketitle

\section*{Motivation}\label{sec:motivation}

Maintaining anonymity online is increasingly difficult.  While
networks like Tor \cite{Dingledine04tor:the} will protect an Internet
Protocol (IP) address at the network layer, it does not protect the
content delivered over Tor.  For example, suppose an author desires to
provide controversial political commentary but wants to remain
anonymous.  In this case, she can protect her IP address with Tor and
use end-to-end encryption to protect her message en-route, but she
could be discovered through stylometry.

Stylometry, a form of authorship recognition, has been found to be
extremely effective especially even at
Internet-scale \cite{Narayanan:2012:FIA:2310656.2310687}.  Thus for
those seeking to publish anonymous writings, not only can the delivery
path reveal them, but their content can as well.  Adversarial
stylometry is the active process of manipulating writing to confuse
the identity of the author.  A set of tools, JStylo and
Anonymouth \cite{conf/pet/McDonaldACSG12}, have been produced by the
Privacy, Security, and Automation Lab (PSAL) at Drexel University to
assist authors in anonymize their writing.

Currently the JStylo and Anonymouth integrated open-source project
(JSAN) is available to download and can be installed on a machine that
runs the Java Virtual Machine (JVM).  While JSAN has been successfully
demonstrated to be effective in assisting authors with adversarial
stylometry \cite{journals/tissec/BrennanAG12}, the constraint of
downloading and installing the software on a machine powerful enough
to run machine learning algorithms on data sets, limits their
adoptability.  We propose increase the availability and usability of
JStylo and Anonymouth by offering them as a web service.

Migrating to a web service would provide JSAN with several benefits.
This web service would provide adversarial stylometry capabilities to
embedded devices like tablets or smart-phones which otherwise could
not run the software natively.  Since there would be no installation,
besides a typical web-browser, a web-service would be better suited
for time-critical situations where an author must quickly anonymize
her document.  Lastly, we believe that a stylometric service could
increase anonymity.

An effective technique in adversarial stylometry is imitation of
another author's writing style.  However, since many are not trained
author imitators, this technique requires significant cognitive effort.
Perhaps a more effective technique, would be to have multiple authors
re-write the target work in their natural style.  This would be
difficult to accomplish with standalone software, but with a web
service with multiple users, this is feasible.

\section*{Approach}\label{sec:approach}

We propose to build a stylometric service around JStylo and
Anonymouth.  However, this project is more than just porting JSAN to
the web.  With a migration to a web service from locally running
software, the anonymity attack vector changes significantly.  We
intend to design and evaluate privacy enhancing techniques for
a stylometric web service.

\subsection{Design}

Our design goal is to increase both the anonymity and availability of
JSAN through this service.  In order to increase the anonymity, we
will need to protect the service from traffic analysis, which we
intend to do by running a Tor hidden service.  To improve the
anonymity and effectiveness of JSAN, we intend to incorporate a
third-party re-writer and in the future, a document mixer.  The
document mixer will randomize the target document, potentially with
other target documents, and present a re-writer the mixed document.
The re-writer will be able to use the Anonymouth-like interface to
anonymize the document without being able to infer the author.  Also,
the mixing will help obfuscate the contents of the document as well.
However, for this initial attempt, we will focus on the third-party
anonymization service.

Although in this initial effort we do not intent to conduct usability
testing, we will consider incentive options for re-writers.  Like
other anonymity networks, we believe that anonymity is improved with a
diverse user base.  The challenge is building the user base.  While we
do not intend to conduct user testing for this initial effort, we will
consider various incentive options like actual payment to
gamification.

\subsection{Implementation}

Our initial idea is to host this service on Amazon Web Services
(AWS).  For the user interface, we are planning to implement the front
end in AngularJS.  Since the existing code is Java, migrating to the
Play Framework seems like a natural progression.  The text editor
functionality will be converted to Firepad, an open source
collaborative editor.  While real-time collaboration is not
necessarily needed, we think that an ``Anonymouth'' user, an
Artificial Agent, would assist the re-writer in edits.

\section*{Related Work}\label{sec:related}
This proposal extends the work from Drexel's PSAL, who have made
several contributions in this field.  In
\cite{conf/pet/McDonaldACSG12}, the authors present the Anonymouth
framework for anonymizing writing.
\cite{Afroz:2012:DHF:2310656.2310711} confirmed adversarial stylometry
is very effective at obfuscated authorship, but also presented
techniques to hide the prescience adversarial stylometry.  Lastly,
\cite{journals/tissec/BrennanAG12} presented successful adversarial
stylometry techniques through obfuscation, imitation, and translation
and produced two corpora of texts.

Tor is one of the most successful anonymity services in
operation \cite{Dingledine04tor:the}.  We intend to protect the
anonymity of users by offering JSAN over a Tor hidden service
however, there has been recent research de-anonymizing popular hidden
services \cite{oakland2013-trawling}.  We will provide a discussion on
the design and experience of enabling a hidden service, but we will
focus on this aspect.

\subsection{Novelty}\label{sec:novelty}

There are two significant contributions as a result of this work.  The
first is a stylometric web service.  This will advance the usability
and capabilities of JSAN and provide a framework for more expansive
user testing in the future.  The second contribution is that this is
the first framework for multi-author adversarial stylometry.  While
single author stylometry has been recently studied, multi-author
documents have not received significant attention.

\section*{Evaluation}\label{sec:evaluation}
This effort is intended to produce several artifacts.  The first is an
evaluation of the privacy architecture of a cloud web service.  Here
we intend to describe the challenges and present and evaluate a
privacy-by-architecture system.  Second, we will provide a survey on
various incentive approaches and suggest a possible method.  Lastly,
we will provide a prototype web service and evaluate it.  Specifically
we will compare the web service to the standalone tools and evaluate
it for accuracy and usability.  Additionally, we will experiment with
the third party anonymization by re-writing each other's writing
samples.  We will provide an evaluation on the perceived difficultly
of re-writing one's own work to that in the mixed system.

\section*{Milestones}\label{sec:milestones}

Table \ref{tab:milestones} contains a proposed timeline for completing
this project.  This work will be split among two developers and there
are several modules that can be independently developed.  In order to
re-architect JSAN, we first need to become familiar with the existing
software.  While this software will be running as a service, we do not
intend to release it to the general public in this time-frame.  We
will conduct the evaluation with perhaps a very limited subset of
other students.

\begin{table}
  \centering
  \begin{tabular}{l | c}
    Milestone & Date\\
    \hline

    Document initial design & October 28\\
    Finish porting JSAN to a web service & November 4\\
    Add the Firebase editro & November 11\\
    Add the third party feature & November 18\\
    Conduct evaluation & November 25\\
    Provide Paper and Presentation & December 2

  \end{tabular}
  \caption{Project Milestones}
  \label{tab:milestones}
\end{table}

\subsection*{Future Work}

The scope of this project is designed to completed in one Drexel
quarter, however we have several ideas for continued work.  With a web
service, we can offer real-time adversarial stylometry.  Assume Alice,
who has a blog, wants to anonymize her next blog post.  She would
connect to our web service, submit the URL for her blog and then write
her next post with adversarial stylometry.  This real-time data
crawling at this scale is simply not feasible with stand alone
software.

Now that a third party will be re-writing documents, we feel that it
is important to obfuscate the content from the re-writer.  One idea,
is to mix the document, perhaps with other documents, prior to
re-writing.  The re-writer would be presented with an otherwise
nonsensical document and would focus on re-write each sentence in her
native style.  The combined document, would contain $n$ author styles,
where $n$ is the number of re-writing authors.

Lastly, for long term adversarial projects, we are curious on how often
one has to re-train the model.  We imagine that a web service could
help monitor the change of a stylometric fingerprint over time.

%%%%%%%%%%
% References and End of Paper
\bibliography{service}
\bibliographystyle{aaai}

\end{document}
%%% Local Variables
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2013-12-04 paper/paper.tex
Enhanced Introduction

--- 2013-10-21 proposal/proposal.tex
@@
 
-\section*{Motivation}\label{sec:motivation}
+\section*{Introduction}\label{sec:intro}
 
@@
 for time-critical situations where an author must quickly anonymize
-her document.  Lastly, we believe that a stylometric service could
-increase anonymity.
+her document.
+
+An example use-case is an author with a time sensitive document that
+she needs to release.  Because of the sensitive nature, she wishes to
+apply adversarial stylometry to her document.  In this case, a
+computer with decent enough performance to natively run machine
+learning techniques may not be available.  However, a web service is
+nearly ubiquitous.
+
+\subsection{Expanding Stylometric Research}
+
+A stylometric web service also expands research opportunities.  This
+service, offered through a modern architecture, would allow
+researchers to easily perform experiments.  An easily accessible tool
+allows for rapid verification of research results and greater
+community engagement.
+
+In addition to convenient access, a web service can provide additional
+diversity in stylometric experimentation.  For example, this web
+service supports multiple authors and provides a better tool for
+real-time, multiple author stylometry than a stand-alone application.
 
@@
 Perhaps a more effective technique, would be to have multiple authors
-re-write the target work in their natural style.  This would be
-difficult to accomplish with standalone software, but with a web
-service with multiple users, this is feasible.
+re-write the target work in their natural style.  While there has been
+numerous studies into single author stylometric analysis, multiple
+authorship is more difficult.  This web services provides a platform
+for multiple authorship research.
+
+\subsection{Challenges in a Web Service}
+
+A privacy enhancing technology that is designed to exist as a web
+service faces different challenges than an application.  Attack
+vectors open up on the service from active denial-of-service attacks
+to passive sniffing.  A privacy web service must take great care to
+ensure that service does not compromise its user's privacy.  In
+Section \ref{sec:design} we provide our architecture and analysis the
+security and privacy.
 

### 2013-12-07 paper/paper.tex
Added section outline
Started to add paragraph on anonymouth architecture.

@@
 security and privacy.
+
+\section{Design}
+
+\subsection{Anonymouth Architecture Review}
+
+The architecture of Anonymouth is that of a conventional desktop
+application.  It uses a layered architecture with essentially two main
+components: the frontend Graphical User Interface (GUI) and the
+backend, consisting of the Weka machine learning toolkit and Jstylo.
+Jystlo is PSAL's stylometric analysis software.   Since Anonymouth was
+designed as a monolithic application, there are direct dependencies
+between the layers without the use of an adaptation layer.
+
+\section{Security Analysis}
+
+\section{Privacy Analysis}
+
+\section{Implementation Details}
+
+\section{Comparison to Stand-alone Application}
+
+\section{Evaluation}
+
+\section{Conclusion}
+
+\section{Proposal stuff --- will be removed}
 

### 2013-12-08 paper/paper.tex
Added architecture qualities.

@@
 between the layers without the use of an adaptation layer.
+
+This design is sufficient for Anonymouth in its current form.  As a
+desktop appliccation, the user can anonymize her and the document
+locally without any additional attack vectors.
+
+\subsection{Requirements for Web Service}
+
+The architecture for a web service imposes different requirements on
+an application.  First and foremost, since Anonymouth is a privacy
+enhancing technology, the web service \emph{must} not degrade the
+privacy protection of the application.  This is a challenge when
+migrating from a desktop to web service since the desktop application
+does not use any networked communicaiton.  However, there is little
+benefit to using Anonymouth on the web if it compromises one's
+privacy.
+
+\subsubsection{Low-latency.}
+The web service should be near-real-time, i.e. low-latency.  We don't
+specify a time requirement but the response should be in the order of
+milliseconds to seconds.  A high latency system would not be well
+suited for a web service.  An example high latency system could simply
+entail sending an encrypted email to a third party who uses Anonymouth
+locally and returns the encrypted result.  While this high-latency
+system seems trivial, note that a naive implementation will reduce the
+user's privacy.  For example, email is very subject to traffic
+analysis (CITE) and encrypted email is easy to detect (CITE),
+therefore this act alone would raise suspiction.  If this third party
+was offering a high-latency anonymiziation service for numerous
+people, the network graph would be easy to detect.
+
+\subsection{Architecture Qualities}
+There are several qualities of a system architecture that are
+considers foundational (CITE lem bass).  These are: availability,
+interoperability, modifiability, performance, security, testability,
+and usability.  In additional we add privacy as an architecture
+quality in our review.
+
+Availability is the measure of the measure of the accesibility and
+realibility of the system, e.g. how well does it handle errors.
+Interoperability refers to the degree with which a system can interact
+with its components or other systems.  Modifiability is important for
+large systems so that they can be easily maintained and scale.  The
+response of the system to input is its performance.  Security is the
+review of a system's ability to protect sensitive data and prevent
+unautorized and undesired behaviour.  Testability is an important
+factor not only in development but also in a deployed system to ensure
+that the system is working as designed.  Usability is notoriously bad
+for security software (CITE How Johnny) and refers to the interaction
+design.  Lastly, by privacy we mean how well a user's anonymitity is
+protected.
+
+In the following sections, we provide an analysis of each quality and
+define the requirements for a stylometric web service.
+
+\subsubsection{Availability.}
+
+If the user can not access the web service, then the user is in the
+same situation as having a device that can not run Anonymouth
+locally.  The entry point to the web service requires a web server.
+Realistically, this service will never see the traffic that FaceBook
+or Twitter experiences, but the web server should be handle thousands
+of requests per day.
+
+A common attack to block availability is a Denial-of-Service (DoS)
+attack.  A DoS attack is akin to receiving a momentarily burst in
+traffic, i.e. the ``Slashdot effect.''  The difference lies in the
+motivation for the sudden attention.  Thus, a service that is
+resistant to DoS attacks also scales well to large second-derivative
+increases in traffic.
+
+There are many implemenation details to achieve availability that are
+beyond the scope of this paper.  We attest that a stylometric service
+needs to be available and should consider the effects of sudden
+traffic increases.
+
+\subsubsection{Interoperability.}
+
+\subsubsection{Modifiability.}
+
+\subsubsection{Performance.}
+
+\subsubsection{Security.}
+
+\subsubsection{Testability.}
+
+\subsubsection{Usability.}
+
+\subsubsection{Privacy.}
 

### 2013-12-08 paper/paper.tex
Added modifiability paragraph.

@@
 
+The stylometric web service should be interoperability with the modern
+web architecture.  Specifically, it should be a service based on
+Representational State Transfer (REST)\cite{Fielding2000}.  REST web
+services define a framework that is client-server, has a uniform
+interface based on HTTP verbs, and supports a layered architecture.
+These features are in-line with the goals of a stylometric web
+service.  Using a REST service, the client software can be a web
+browser, which is nearly ubiqiteious on mobile devices.
+
 \subsubsection{Modifiability.}
+
+One of the goals of the service is provide a platform for stylometric
+research.  In this sense in must be modifable to accomodate different
+kinds of experiments including ones not currently anticipated.
+Software engineering best pratices are applicable here mainly having
+well abstracted interfaces and modular components.  As a RESTful web
+service, each endpoint should have a concise application programming
+interface (API) for a given feature set.  For example, there should be
+a stylometry endpoint that can process text and return features.
+Other services, such as an adversarial stylometry service, should use
+the stylometric service via its REST API.
+
+A web service has a distinct advantage here over the modifiability of
+the desktop software.  One can deploy an updated version of the
+software by pushing the update to servers and instantly clients will
+have the new version.  As a research platform, this is a very valuable
+feature.  For example, split testing or A/B testing, is much easier to
+control and manage with a web service than packaged software.
 

### 2013-12-08 paper/paper.tex
Paper improvements for implementation and security

@@
 
+The performance of the Stylometry Service
+
 \subsubsection{Security.}
 
+A number of attack vectors for the web application currently exist. We
+discuss those which seem most significant here below. However one key
+security implication of a web-delivered Stylometry Service is that it
+is expected to be delivered over the web, can be accessed in this configuration by anyone with knowledge of its unique URL (or .onion
+address). This allows adversaries greater opportunity to attempt to
+penetrate the security of the web application relative to a client
+application installed on a PC that is not internet connected.
+
+It is expected that, before the service would be used in a real-world
+use case, a user would configure and deploy supporting databases
+associated with the login and SSL options available in the
+Play Framework.
+
+Although web accessbility may be a significant risk from a usability
+standpoint, the anecdotal infrequency with which adversarial
+stylometry software is used even among privacy-conscious users as
+determined by conversations with colleagues of the authors
+suggests that delivery of this functionality via a web page (or even
+potentially via a browser plugin functional across multiple web pages)
+may be an appropriate trade-off to make.
+
+Beyond the concerns mentioned above, a number of specific attack
+vectors remain for a stylometric web service in general and for our
+implementation in particular:
+
+Man in the middle attacks: If a user accepts a rogue SSL certificate, it
+may be possible to create a "man in the middle" attack where the user
+believes he/she is communicating with a specific Stylometry Service,
+but is infact communicating via an impersonated target.
+
+Replay attacks: An evesdropper may 'replay' a message to the
+webservice in an attempt to surrepituously revert parts of the text to
+earlier versions. This may be possible as it is not documented whether
+the current implementation uses nonces when transmitting messages.
+
+HTML5 Canvas attacks: The etherpad implementation uses the new
+'canvas' element introduced in HTML5 extensively. Recently an attack
+has been documented
+(http://www.contextis.com/files/Browser_timing_Attacks.pdf) whereby
+Firefox optimizations in the implementation of the
+requestAnimationFrame method have been used by to detect differences
+in link coloring across frames (allowing an adversary to determine if
+a particular styometry service has been visited, for instance)
+
+Note: We do not know if any of these vectors allows for a specific
+attack, but suggest they should be considered for any future
+implementation research in the area of stylometric web services using
+a similar architecture.
+
 \subsubsection{Testability.}
+
+The web service UI is amenable to automated testing via web testing
+frameworks such as Selenium (although such tests were not written for
+this project). JUnit tests, in contrast, were written to test both
+service method paths implemented. The authors consider the fact that
+this application is delivered as a web application with a distinct
+service layer to be a positive from the standpoint of testability, as
+it allows users who may wish to modify the service the ability to
+expand an existing unit test suite.
 
@@
 
-\section{Privacy Analysis}
+\section{Privacy and Anonymity Analysis}
+
+The privacy of a user accessing the web service is expected to be
+ensured via the use of TLS/SSL encryption for all data transmitted
+between the client and server. The anonymity of the user is expected
+to be promoted via the use of an Onion Routing protocol such as Tor,
+to ensure that the IP of the client cannot be directly linked to the
+IP of the service.
 
@@
 
+We implemented a web application based on the Play Web Application
+Framework in Java. This web application had a reference to a modified
+version of JSAN which was forked from the PSAL Anonymouth repository
+(https://github.com/psal/anonymouth) on September 29, 2013. In
+addition the application has major dependencies on JQuery, Twitter
+Bootstrap (for page layout), and Etherpad  (an open-source collaborative text editing
+web application and library). Etherpad (specifically Etherpad Lite is
+the version used here) in turn has major dependencies on
+node.js for building and running the backend service.
+
+At a high level the implementation is as follows: A user browses to
+the Stylometry Service via a web browser. This causes the Play
+Framework web application to serve up a web page with an Etherpad control
+and instructions for the user to enter in the document they wish to
+anonymize. The etherpad control is implemented as an iframe which
+serves an Etherpad that is connected to the node.js server running the
+Etherpad backend (both servers should reside on the same domain,
+running on different ports). The page served by Play also contains a
+button which allows the author to specify when he or she would like to
+submit the document for anonymization to Anonymouth. Because the
+Anonymouth analysis process depends on a number of
+computationally-intensive algorithms (among them running SMO analysis
+in Weka as well as a Basic-9 feature stylometric analysis) we
+implemented this calculation asynchronously. When a user clicks the
+button to run an analysis, JQuery is used to issue a HTTP POST
+containing in the message body a JSON-encoded
+representation of the current Etherpad text to an endpoint at
+/getAnonymouthInfoJSON. During the time that the Anonymouth analysis
+is underway, a spinner control from the spin.js library is used to
+indicate to the user than an analysis is underway. The fact that the
+request is made to Anonymouth asynchronously allows a user to continue
+editing the text while an analysis is running, allowing for a smooth
+user experience.
+
+The web service as implemented currently supports only 1 author as the assumption is
+made that the author has pre-configured the "doc set" (also referred
+to as 'problem set' in Anonymouth source) that provides references as
+to the author's own writing style, as well as writing samples for
+other authors that will be used as a reference for writing styles that
+are different than that of the active author. The user can
+additionally configure the anonymouth properties file
+(anonymouthprop.prop) in the jsan resources directory to influence
+settings such as the feature set to use for stylometric identification
+as well as the number of threads to use and maximum number of features
+to analyze.
+
+One configured, the call to the getAnonymouthInfoJSON input will
+overwrite the "test.txt" file on disk that is configured in the provided problem
+set. This will ensure that changing the document in Etherpad forces an
+update to the test file and thus ensuring that the 'latest' document
+is always anonymized. Once the problem set has been updated, the
+'Anonymouth library' is invoked. The 'Anonymouth library' is a forked
+version of the current Anonymouth application, which is designed to be
+used behind a Swing/AWT rich client GUI. A number of implementation
+challenges were present when trying to separate the core anonymization
+logic of Anonymouth from its GUI implementation - most specifically,
+although an 'engine' namespace exists which holds much of the
+anonymization logic, significant dependencies still existed between
+the 'engine' and the 'GUI' namespaces, specifically in the event
+handlers associated with the Editor screen and the GUIMain classes. Much of the work in this
+project consisted of reducing the coupling between these two
+namespaces.
+
+As much of the configuration logic was handled at the GUI layer (via
+ThePresident and GUIMain classes) we took the approach of refactoring
+the GUI layer to work in a 'headless' mode, that is, without any
+windows launching. Long-term it would be preferable to have no
+dependencies on the GUI namespace at all for the Stylometry Service,
+however this could not be achieved in the available timeframe for this
+project. The web service thus invokes a modified version of the
+ThePresident class, which coordinates reading configuration files,
+loading the configured problem set, and using numerous libraries
+(JGAAP and Weka among them) to conduct an adversarial stylometric
+analysis. The results are returned by the web service in the form of a
+JSON-encoded list of words to remove, as well as an indication of
+'changes needed' to the current text to reach an acceptable level of
+anonynmity.
+
+While this analysis has been running, the UI has been waiting on a
+response to the request made of the Stylometric Service. Once this
+request is returned, a request is made to spin.js library to stop the
+spinner, and JQuery is again used to update a div on the page with the
+results of the adversarial stylometric analysis. The JQuery Promises
+interface was used to ensure that the UI correctly waited for these
+otherwise asynchronous requests to be completed in the right order.
+
+The web application (bundled with all dependencies) can be downloaded
+by cloning https://github.com/LRParser/anonymouth and running the
+following command:
+
+./bootstrap.sh
+
+This command will copy the latest JSAN JAR files to the 'lib'
+directory of the Play Framework Web Application, start a Play
+Framework Server on port 9000, and start an Etherpad Lite server on
+port 9001 over node.js.
+
 \section{Comparison to Stand-alone Application}
 
+The stand-alone application has both advantages and disadvantages
+relative to the web service. To start with advantages: it contains
+more robust error handling, offers a GUI to create a problem set, and
+provides a richer editing experience for anonymized
+texts. Disadvantages concern ease of use (users must download and
+execute a JAR file) and supported platforms (it is unlikely that this
+JAR file will be supported on many mobile phones, for instance). The
+Stylometry Service, in contrast, is potentially more accessible than
+the standalone application: it can be accessed via mobile phones and
+tablets, for instance. Likewise application delivery may be simpler -
+nothing must be downloaded locally. Furthermore, the web application
+maintains a 'timeline' of changes made to a text and also allows for
+simple multi-party anonymization of documents.
+
+Disadvantages to the web application include the fact that it offers fewer anonymization
+features (for instance, highlighting of specific text passages),
+instead focusing primarily on 'words to remove'. Furthermore, its
+security footprint is less well known, as it introduces a number of
+new dependencies / potential attack vectors such as JQuery, Twitter
+Bootstrap, Etherpad Lite, node.js, etc.
+
+For a user likely to be using
+mobile devices or a casual user looking to quickly anonymize texts,
+we suggest that the web interface may be a better option. For a user
+facing a highly sophisticated adversary and needing detailed
+anonymization suggestions, we suggest that the stand-alone application
+may be a better option. We note that there is no technical reason that
+could keep the web application from offering all of the same
+anonymization suggestions as the standalone application, and thus is
+may be the case that in the future the web application could be
+recommendable to a wider range of users.
+standalone client
+
 \section{Evaluation}
+
+Although time didn't permit detailed user testing of the web
+application, the authors did conduct one experiment with two users
+using Amazon Mechanical Turk. Users were given 45 minutes to anonymize
+a document. The title of the request was "Help re-phrase approx. 500
+word texts as part of a research project". Specifically users were
+asked, 'Re-phrase the text in the below-linked document while keeping
+the original meeting. Substitute synonyms, change punctuation (I am to
+I'm), split up / join sentences, etc. This is part of a research
+project to see how well different persons can make a text appear as if
+it wasn't written by the original author.'
+
+The responses of users on Mechanical Turk (who were trying to
+anonymize a text without any supporting software) were compared with
+anonymization attempts by the authors of this paper against the same
+document. The anonymization attempts by the authors took place before
+reviewing the submissions from Mechanical Turk. For one sample paper,
+d 09.txt from the Brennan-Greenstadt corpus (Michael Brennan and Rachel Greenstadt.
+Practical Attacks Against Authorship Recognition Techniques in Proceedings of the Twenty-First Conference on Innovative Applications of Artificial Intelligence (IAAI), Pasadena, California, July 2009.
+), we noted that Anonymouth returned a "changes needed" score
+on the original document of 2.518, 2.677 for the users 'naive' attempt
+to anonymize over Mechanical Turk, and 2.467 for the attempt of one of
+the authors to anonymize using the web application created in this
+paper. Each of the two anonymization attempts for the 500-word
+document took approximately 15 minutes. Although these results are far from achieving statistical
+significance, they do suggest that it may be possible to use this
+software to achieve anonymization levels which surpass those of a
+'naive' anonymization attempt.
 

### 2013-12-08 paper/paper.tex
Updated performance notes

@@
 \subsubsection{Low-latency.}
-The web service should be near-real-time, i.e. low-latency.  We don't
-specify a time requirement but the response should be in the order of
-milliseconds to seconds.  A high latency system would not be well
+The web service as implemented is near-real-time, i.e. low-latency,
+bounded primarily be the performance of Anonymouth. One key feature of
+the current implementation is the asynchronous processing of
+stylometric information, which allows a user to continually modify a
+text while anonymity information is calculated in the background. The
+latency of the response times for each stylometric analysis is on the
+order of 1 to 2 minutes in the default configuration (see Performance
+section for futher details).
+
+A high latency system would not be well
 suited for a web service.  An example high latency system could simply
@@
 
-The stylometric web service should be interoperability with the modern
+The stylometric web service we implemented is interoperable with the modern
 web architecture.  Specifically, it should be a service based on
@@
 
-The performance of the Stylometry Service
+The performance of the Stylometry Service as implemented is largely
+determined by that of the Anonymouth service that it uses to get
+stylometry suggestions. For an analysis of 1 500-word test document vs
+23 documents from 4 'other' authors and using 8 training documents
+from the to-anonymize author, we recorded a total of 67 seconds
+required for the Anonymouth analysis, with less than 1 additional
+second used to update the client UI, on a 3.3 Ghz Core i5 Ubuntu 12.04
+Desktop machine, using 1 calculation thread for Anonymouth. These results suggests that any attempts at
+performance optimization should center around optimizing the
+performance of the Anonymouth configuration.
+
+After each stylometric analysis is complete, the web service ensures
+all relevant anonymouth resources are closed. This allows the web
+service to be used over a long period of time (20 or more
+anonymization attempts have been tested) without memory leaks noted.
+
+Further performance testing and optimization is required in order to support a true
+multi-user service. The authors would suggest using a web service
+based load test framework, such as Apache's JMeter or LoadUI, in order
+to fully test the service under various potential user loads.
 
@@
 'canvas' element introduced in HTML5 extensively. Recently an attack
-has been documented
-(http://www.contextis.com/files/Browser_timing_Attacks.pdf) whereby
+has been documented (see Contextis Browser Timing Attacks white paper) whereby
 Firefox optimizations in the implementation of the
@@
 
-\section{Evaluation}
+\section{Single User Evaluation}
 
@@
 
+\section{Multiple Concurrent User Evaluation}
+
+TODO
+
 \section{Conclusion}
 
-\section{Proposal stuff --- will be removed}
-
-\section*{Approach}\label{sec:approach}
-
-We propose to build a stylometric service around JStylo and
-Anonymouth.  However, this project is more than just porting JSAN to
-the web.  With a migration to a web service from locally running
-software, the anonymity attack vector changes significantly.  We
-intend to design and evaluate privacy enhancing techniques for
-a stylometric web service.
-
-\subsection{Design}
-
-Our design goal is to increase both the anonymity and availability of
-JSAN through this service.  In order to increase the anonymity, we
-will need to protect the service from traffic analysis, which we
-intend to do by running a Tor hidden service.  To improve the
-anonymity and effectiveness of JSAN, we intend to incorporate a
-third-party re-writer and in the future, a document mixer.  The
-document mixer will randomize the target document, potentially with
-other target documents, and present a re-writer the mixed document.
-The re-writer will be able to use the Anonymouth-like interface to
-anonymize the document without being able to infer the author.  Also,
-the mixing will help obfuscate the contents of the document as well.
-However, for this initial attempt, we will focus on the third-party
-anonymization service.
-
-Although in this initial effort we do not intent to conduct usability
-testing, we will consider incentive options for re-writers.  Like
-other anonymity networks, we believe that anonymity is improved with a
-diverse user base.  The challenge is building the user base.  While we
-do not intend to conduct user testing for this initial effort, we will
-consider various incentive options like actual payment to
-gamification.
-
-\subsection{Implementation}
-
-Our initial idea is to host this service on Amazon Web Services
-(AWS).  For the user interface, we are planning to implement the front
-end in AngularJS.  Since the existing code is Java, migrating to the
-Play Framework seems like a natural progression.  The text editor
-functionality will be converted to Firepad, an open source
-collaborative editor.  While real-time collaboration is not
-necessarily needed, we think that an ``Anonymouth'' user, an
-Artificial Agent, would assist the re-writer in edits.
+There are two significant contributions as a result of this work.  The
+first is a stylometric web service.  This advances the usability
+and capabilities of JSAN and provide a framework for more expansive
+user testing in the future. The user testing results suggest that a
+web interface may offer usability advantages while still providing a
+meaningful increase in author anonymity.  The second contribution is that this is
+the first framework for multi-author adversarial stylometry.  Our
+results here suggest TODO.
 
@@
 focus on this aspect.
-
-\subsection{Novelty}\label{sec:novelty}
-
-There are two significant contributions as a result of this work.  The
-first is a stylometric web service.  This will advance the usability
-and capabilities of JSAN and provide a framework for more expansive
-user testing in the future.  The second contribution is that this is
-the first framework for multi-author adversarial stylometry.  While
-single author stylometry has been recently studied, multi-author
-documents have not received significant attention.
-
-\section*{Evaluation}\label{sec:evaluation}
-This effort is intended to produce several artifacts.  The first is an
-evaluation of the privacy architecture of a cloud web service.  Here
-we intend to describe the challenges and present and evaluate a
-privacy-by-architecture system.  Second, we will provide a survey on
-various incentive approaches and suggest a possible method.  Lastly,
-we will provide a prototype web service and evaluate it.  Specifically
-we will compare the web service to the standalone tools and evaluate
-it for accuracy and usability.  Additionally, we will experiment with
-the third party anonymization by re-writing each other's writing
-samples.  We will provide an evaluation on the perceived difficultly
-of re-writing one's own work to that in the mixed system.
-
-\section*{Milestones}\label{sec:milestones}
-
-Table \ref{tab:milestones} contains a proposed timeline for completing
-this project.  This work will be split among two developers and there
-are several modules that can be independently developed.  In order to
-re-architect JSAN, we first need to become familiar with the existing
-software.  While this software will be running as a service, we do not
-intend to release it to the general public in this time-frame.  We
-will conduct the evaluation with perhaps a very limited subset of
-other students.
 

### 2013-12-09 paper/paper.tex
Fixed some references.

@@
 Currently the JStylo and Anonymouth integrated open-source project
-(JSAN) is available to download and can be installed on a machine that
+(JSAN) \cite{BrennanG09}, \cite{journals/tissec/BrennanAG12},
+\cite{conf/pet/McDonaldACSG12} is available to download and can be installed on a machine that
 runs the Java Virtual Machine (JVM).  While JSAN has been successfully
@@
 
-A high latency system would not be well
-suited for a web service.  An example high latency system could simply
-entail sending an encrypted email to a third party who uses Anonymouth
-locally and returns the encrypted result.  While this high-latency
-system seems trivial, note that a naive implementation will reduce the
-user's privacy.  For example, email is very subject to traffic
-analysis (CITE) and encrypted email is easy to detect (CITE),
-therefore this act alone would raise suspiction.  If this third party
-was offering a high-latency anonymiziation service for numerous
-people, the network graph would be easy to detect.
+A high latency system would not be well suited for a web service.  An
+example high latency system could simply entail sending an encrypted
+email to a third party who uses Anonymouth locally and returns the
+encrypted result.  While this high-latency system seems trivial, note
+that a naive implementation will reduce the user's privacy.  For
+example, email is very subject to traffic analysis
+\cite{Mathewson04practicaltraffic} and encrypted email is easy to
+detect, therefore this act alone would raise suspiction.  If
+this third party was offering a high-latency anonymiziation service
+for numerous people, the network graph would be easy to detect.
 
@@
 There are several qualities of a system architecture that are
-considers foundational (CITE lem bass).  These are: availability,
+considers foundational\cite{Bass:2012:SAP:2392670}.  These are: availability,
 interoperability, modifiability, performance, security, testability,
@@
 that the system is working as designed.  Usability is notoriously bad
-for security software (CITE How Johnny) and refers to the interaction
-design.  Lastly, by privacy we mean how well a user's anonymitity is
-protected.
+for security software \cite{Whitten:1999:WJC:1251421.1251435} and
+refers to the interaction design.  Lastly, by privacy we mean how well
+a user's anonymitity is protected.
 
@@
 
-The performance of the Stylometry Service as implemented is largely
-determined by that of the Anonymouth service that it uses to get
-stylometry suggestions. For an analysis of 1 500-word test document vs
-23 documents from 4 'other' authors and using 8 training documents
-from the to-anonymize author, we recorded a total of 67 seconds
-required for the Anonymouth analysis, with less than 1 additional
-second used to update the client UI, on a 3.3 Ghz Core i5 Ubuntu 12.04
-Desktop machine, using 1 calculation thread for Anonymouth. These results suggests that any attempts at
-performance optimization should center around optimizing the
-performance of the Anonymouth configuration.
+\subsubsection{Security.}
 
-After each stylometric analysis is complete, the web service ensures
-all relevant anonymouth resources are closed. This allows the web
-service to be used over a long period of time (20 or more
-anonymization attempts have been tested) without memory leaks noted.
+\subsubsection{Testability.}
 
-Further performance testing and optimization is required in order to support a true
-multi-user service. The authors would suggest using a web service
-based load test framework, such as Apache's JMeter or LoadUI, in order
-to fully test the service under various potential user loads.
+\subsubsection{Usability.}
 
-\subsubsection{Security.}
+\subsubsection{Privacy.}
+
+\section{Security Analysis}
 
@@
 
-Man in the middle attacks: If a user accepts a rogue SSL certificate, it
+{\bf Man in the middle attacks}: If a user accepts a rogue SSL certificate, it
 may be possible to create a "man in the middle" attack where the user
@@
 
-Replay attacks: An evesdropper may 'replay' a message to the
+{\bf Replay attacks}: An evesdropper may 'replay' a message to the
 webservice in an attempt to surrepituously revert parts of the text to
@@
 
-HTML5 Canvas attacks: The etherpad implementation uses the new
+{\bf HTML5 Canvas attacks}: The etherpad implementation uses the new
 'canvas' element introduced in HTML5 extensively. Recently an attack
-has been documented (see Contextis Browser Timing Attacks white paper) whereby
-Firefox optimizations in the implementation of the
-requestAnimationFrame method have been used by to detect differences
-in link coloring across frames (allowing an adversary to determine if
-a particular styometry service has been visited, for instance)
+has been documented \cite{BrowserTiming} whereby Firefox optimizations
+in the implementation of the requestAnimationFrame method have been
+used by to detect differences in link coloring across frames (allowing
+an adversary to determine if a particular styometry service has been
+visited, for instance)
 
@@
 a similar architecture.
-
-\subsubsection{Testability.}
-
-The web service UI is amenable to automated testing via web testing
-frameworks such as Selenium (although such tests were not written for
-this project). JUnit tests, in contrast, were written to test both
-service method paths implemented. The authors consider the fact that
-this application is delivered as a web application with a distinct
-service layer to be a positive from the standpoint of testability, as
-it allows users who may wish to modify the service the ability to
-expand an existing unit test suite.
-
-\subsubsection{Usability.}
-
-\subsubsection{Privacy.}
-
-\section{Security Analysis}
 
@@
 
+\section{Evaluation of Architecture Qualities}
+
+\subsection{Performance.}
+
+The performance of the Stylometry Service as implemented is largely
+determined by that of the Anonymouth service that it uses to get
+stylometry suggestions. For an analysis of 1 500-word test document vs
+23 documents from 4 'other' authors and using 8 training documents
+from the to-anonymize author, we recorded a total of 67 seconds
+required for the Anonymouth analysis, with less than 1 additional
+second used to update the client UI, on a 3.3 Ghz Core i5 Ubuntu 12.04
+Desktop machine, using 1 calculation thread for Anonymouth. These results suggests that any attempts at
+performance optimization should center around optimizing the
+performance of the Anonymouth configuration.
+
+After each stylometric analysis is complete, the web service ensures
+all relevant anonymouth resources are closed. This allows the web
+service to be used over a long period of time (20 or more
+anonymization attempts have been tested) without memory leaks noted.
+
+Further performance testing and optimization is required in order to support a true
+multi-user service. The authors would suggest using a web service
+based load test framework, such as Apache's JMeter or LoadUI, in order
+to fully test the service under various potential user loads.
+
+\subsection{Testability.}
+
+The web service UI is amenable to automated testing via web testing
+frameworks such as Selenium (although such tests were not written for
+this project). JUnit tests, in contrast, were written to test both
+service method paths implemented. The authors consider the fact that
+this application is delivered as a web application with a distinct
+service layer to be a positive from the standpoint of testability, as
+it allows users who may wish to modify the service the ability to
+expand an existing unit test suite.
+
 \section{Conclusion}

### 2013-12-09 paper/paper.tex
Add deploy info

--- 2013-12-08 paper/paper.tex
@@
 
+\section{Deployment}
+
+The web application can be deployed via the following commands on a
+Ubuntu 12.04 desktop installation:
+
+sudo apt-get update
+sudo apt-get install ubuntu-desktop ant openjdk-7-jdk postgresql git
+sudo add-apt-repository ppa:chris-lea/node.js
+sudo apt-get update
+sudo apt-get install nodejs
+
+# Clone Repository
+
+git clone https://github.com/LRParser/anonymouth.git
+
+# Start service
+cd anonymouth
+./bootstrap.sh
+
 \section{Single User Evaluation}

### 2013-12-10 paper/paper.tex
Added paper to .gitignore and added listing package.

--- 2013-12-09 paper/paper.tex
@@
 \usepackage{url}
+\usepackage{listings}
+\usepackage{graphicx}
+\usepackage{verbatim} % used to display code
+\usepackage{hyperref}
+%\usepackage{fullpage}
+\usepackage[ansinew]{inputenc} % german umlauts
+\usepackage[usenames,dvipsnames]{color}
+\usepackage{float}
+\usepackage{subfig}
+\usepackage{tikz}
+\usetikzlibrary{calc,through,backgrounds}
+\usepackage{fancyvrb}
+\usepackage{acronym}
+\usepackage{amsthm} % Uuhhh yet another package
+\VerbatimFootnotes % Required, otherwise verbatim does not work in footnotes!
+%\usepackage{listings}
+
+\definecolor{Brown}{cmyk}{0,0.81,1,0.60}
+\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
+\definecolor{CadetBlue}{cmyk}{0.62,0.57,0.23,0}
+\definecolor{lightlightgray}{gray}{0.9}
 
 \begin{document}
+
+\lstset{
+language=bash,                          % Code langugage
+basicstyle=\ttfamily,                   % Code font, Examples: \footnotesize, \ttfamily
+keywordstyle=\color{OliveGreen},        % Keywords font ('*' = uppercase)
+commentstyle=\color{gray},              % Comments font
+numbers=left,                           % Line nums position
+numberstyle=\tiny,                      % Line-numbers fonts
+stepnumber=1,                           % Step between two line-numbers
+numbersep=5pt,                          % How far are line-numbers from code
+backgroundcolor=\color{lightlightgray}, % Choose background color
+frame=none,                             % A frame around the code
+tabsize=2,                              % Default tab size
+captionpos=b,                           % Caption-position = bottom
+breaklines=true,                        % Automatic line breaking?
+breakatwhitespace=false,                % Automatic breaks only at whitespace?
+showspaces=false,                       % Dont make spaces visible
+showtabs=false,                         % Dont make tabls visible
+columns=flexible,                       % Column format
+morekeywords={__global__, __device__},  % CUDA specific keywords
+}
 
@@
 
+\section{Deployment}
+
+The web application can be deployed via the following commands on a
+Ubuntu 12.04 desktop installation:
+
+\begin{lstlisting}[caption={Install Dependencies},label={lst:install}]
+sudo apt-get update
+sudo apt-get install ubuntu-desktop ant openjdk-7-jdk postgresql git
+sudo add-apt-repository ppa:chris-lea/node.js
+sudo apt-get update
+sudo apt-get install nodejs
+git clone https://github.com/LRParser/anonymouth.git
+\end{lstlisting}
+
+\begin{lstlisting}[caption={Start Service},label={lst:start}]
+cd anonymouth
+./bootstrap.sh
+\end{lstlisting}
+
 \section{Single User Evaluation}

### 2013-12-11 paper/paper.tex
Added reference, filling in section.

@@
 (JSAN) \cite{BrennanG09}, \cite{journals/tissec/BrennanAG12},
-\cite{conf/pet/McDonaldACSG12} is available to download and can be installed on a machine that
-runs the Java Virtual Machine (JVM).  While JSAN has been successfully
-demonstrated to be effective in assisting authors with adversarial
-stylometry \cite{journals/tissec/BrennanAG12}, the constraint of
-downloading and installing the software on a machine powerful enough
-to run machine learning algorithms on data sets, limits their
-adoptability.  We propose increase the availability and usability of
-JStylo and Anonymouth by offering them as a web service.
+\cite{conf/pet/McDonaldACSG12} is available to download and can be
+installed on a machine that runs the Java Virtual Machine (JVM).
+While JSAN has been successfully demonstrated to be effective in
+assisting authors with adversarial stylometry
+\cite{journals/tissec/BrennanAG12}, the constraint of downloading and
+installing the software on a machine powerful enough to run machine
+learning algorithms on data sets, limits their adoptability.  We
+propose increase the availability and usability of JStylo and
+Anonymouth by offering them as a web service.
 
@@
 
+We do not place an specific performance metrics on the service other
+than that it should be reasonably responsive.  Since JStylo relies on
+Weka \cite{Hall:2009:WDM:1656274.1656278} to implement the machine
+learning algorithms, this server should have a decent amount of RAM.
+
 \subsubsection{Security.}
+
+The security features need for a stylometric service are
+authentication, confidentiality, integrity, and repudiation.
+
+{\bf Authentication.}  Users must be able to authenticate the
+service.  We propose that if the service is using HTTPS with a server
+certificate signed by a trusted certificate authority that this will
+suffice.  However, when running behind a Tor Hidden Service, this is
+slightly more complicated.  The service can sign the onion address
+that it provides and Tor will ensure that the address maps to the
+service.  The signature would correspond to a trusted certificate
+authority issued certificate.  Mutual authentication, or
+authentication of the users should \emph{not} be conducted as this
+would either compromise the user's identity.
+
+{\bf Confidentiality.} The service must protect the confidentiality of
+the user's data.  The user is trusting the service with their corpus
+and document to anonymize and that must be revealed to unauthroized
+users.  However, one of the goals of this service is to allow multiple
+authors to collaborate.  In this case, the confidentiality
+requirements are more interesting.  We don't specifiy an
+implementation, but there are various techniques that could satisfy
+this requirement.
+
+Besides multi-authors, the service is also multi-user.
 
@@
 security implication of a web-delivered Stylometry Service is that it
-is expected to be delivered over the web, can be accessed in this configuration by anyone with knowledge of its unique URL (or .onion
+is expected to be delivered over the web, can be accessed in this
+configuration by anyone with knowledge of its unique URL (or .onion
 address). This allows adversaries greater opportunity to attempt to

### 2013-12-11 paper/paper.tex
Added figures and some more text.

@@
 designed as a monolithic application, there are direct dependencies
-between the layers without the use of an adaptation layer.
+between the layers without the use of an adaptation layer.  Figure
+\ref{fig:jsan} illustrates the architecture in a layered drawing.  In
+this drawing, components, represented as boxes, can call software
+below and to the right.
 
@@
 locally without any additional attack vectors.
+
+\begin{figure}
+  \centering
+    \includegraphics[width=0.4\textwidth]{img/jsan.pdf}
+  \caption{Existing JSAN Architecture}
+  \label{fig:jsan}
+\end{figure}
 
@@
 
-Besides multi-authors, the service is also multi-user.
+Besides multi-authors, the service is also multi-user.  Thus, the
+user's document is loaded into RAM with other user's documents.
+Therefore, the service is vulnerable to memory dump attacks.  Assuming
+that the service runs on a third party provide, like Amazon Web
+Services, it is also vulnerable to malicious insiders
+\cite{conf/dsn/RochaC11}.
+
+{\bf Integrity.}  The service must maintain the integrity of the
+corpus and the target document.  This not only includes integrity in
+transit but also the integrity of the presented document to the user.
+Using Transport Layer Security (TLS), the integrity is guaranteed
+during transit.
+
+{\bf Repudiation.}  The service must not assign long-term identity
+to any operations.  Therefore, TLS connections must use ephemeral
+keys to provide Perfect Forward Secrecy (PFS).  The service must not
+maintain logs that will identify the target document, the corpus, or
+the users of the service.
 
 \subsubsection{Testability.}
+
+The service must be modular in design to support testing of each
+endpoint.  While adopting the full Netflix-like approach may be
+over-engineering for this limited web-service,
+\cite{Tseitlin:2013:AO:2492007.2492022}, there are certainly aspects
+of their design that are applicable.  For example the service should
+be resilient to service outages.  If the service is unavailable, it
+can not protect the anonymity of authors.
 
@@
 
+\subsection{Example Architecture}
+
+\begin{figure*}
+  \centering
+    \includegraphics[width=0.6\textwidth]{img/jsanaas.pdf}
+  \caption{Example JSANaaS Architecture as a Deployment Diagram}
+  \label{fig:jsanaas}
+\end{figure*}
 \section{Security Analysis}
@@
 
-{\bf Man in the middle attacks}: If a user accepts a rogue SSL certificate, it
-may be possible to create a "man in the middle" attack where the user
-believes he/she is communicating with a specific Stylometry Service,
-but is infact communicating via an impersonated target.
+{\bf Man in the middle attacks}: If a user accepts a rogue SSL
+certificate, it may be possible to create a "man in the middle" attack
+where the user believes she is communicating with a specific
+Stylometry Service, but is infact communicating via an impersonated
+target.
 
-{\bf Replay attacks}: An evesdropper may 'replay' a message to the
+{\bf Replay attacks}: An evesdropper may replay a message to the
 webservice in an attempt to surrepituously revert parts of the text to
@@
 an adversary to determine if a particular styometry service has been
-visited, for instance)
+visited, for instance).
 
@@
 version of JSAN which was forked from the PSAL Anonymouth repository
-(https://github.com/psal/anonymouth) on September 29, 2013. In
-addition the application has major dependencies on JQuery, Twitter
-Bootstrap (for page layout), and Etherpad  (an open-source collaborative text editing
-web application and library). Etherpad (specifically Etherpad Lite is
-the version used here) in turn has major dependencies on
-node.js for building and running the backend service.
+\cite{PSAL:github}. In addition the application has major dependencies
+on JQuery, Twitter Bootstrap (for page layout), and Etherpad (an
+open-source collaborative text editing web application and library)
+\cite{etherpad}. Etherpad (specifically Etherpad Lite is the version
+used here) in turn has major dependencies on node.js for building and
+running the backend service.
 
@@
 the Stylometry Service via a web browser. This causes the Play
-Framework web application to serve up a web page with an Etherpad control
-and instructions for the user to enter in the document they wish to
-anonymize. The etherpad control is implemented as an iframe which
-serves an Etherpad that is connected to the node.js server running the
-Etherpad backend (both servers should reside on the same domain,
-running on different ports). The page served by Play also contains a
-button which allows the author to specify when he or she would like to
-submit the document for anonymization to Anonymouth. Because the
-Anonymouth analysis process depends on a number of
-computationally-intensive algorithms (among them running SMO analysis
-in Weka as well as a Basic-9 feature stylometric analysis) we
+Framework web application to serve up a web page with an Etherpad
+control and instructions for the user to enter in the document they
+wish to anonymize. The etherpad control is implemented as an iframe
+which serves an Etherpad that is connected to the node.js server
+running the Etherpad backend (both servers should reside on the same
+domain, running on different ports). The page served by Play also
+contains a button which allows the author to specify when he or she
+would like to submit the document for anonymization to
+Anonymouth. Because the Anonymouth analysis process depends on a
+number of computationally-intensive algorithms (among them running SMO
+analysis in Weka as well as a Basic-9 feature stylometric analysis) we
 implemented this calculation asynchronously. When a user clicks the
 button to run an analysis, JQuery is used to issue a HTTP POST
-containing in the message body a JSON-encoded
-representation of the current Etherpad text to an endpoint at
-/getAnonymouthInfoJSON. During the time that the Anonymouth analysis
-is underway, a spinner control from the spin.js library is used to
-indicate to the user than an analysis is underway. The fact that the
-request is made to Anonymouth asynchronously allows a user to continue
-editing the text while an analysis is running, allowing for a smooth
-user experience.
+containing in the message body a JSON-encoded representation of the
+current Etherpad text to an endpoint at
+\url{/getAnonymouthInfoJSON}. During the time that the Anonymouth
+analysis is underway, a spinner control from the spin.js library is
+used to indicate to the user than an analysis is underway. The fact
+that the request is made to Anonymouth asynchronously allows a user to
+continue editing the text while an analysis is running, allowing for a
+smooth user experience.
 
-The web service as implemented currently supports only 1 author as the assumption is
-made that the author has pre-configured the "doc set" (also referred
-to as 'problem set' in Anonymouth source) that provides references as
-to the author's own writing style, as well as writing samples for
-other authors that will be used as a reference for writing styles that
-are different than that of the active author. The user can
+The web service as implemented currently supports only 1 author as the
+assumption is made that the author has pre-configured the "doc set"
+(also referred to as 'problem set' in Anonymouth source) that provides
+references as to the author's own writing style, as well as writing
+samples for other authors that will be used as a reference for writing
+styles that are different than that of the active author. The user can
 additionally configure the anonymouth properties file
-(anonymouthprop.prop) in the jsan resources directory to influence
+(\texttt{anonymouthprop.prop}) in the jsan resources directory to influence
 settings such as the feature set to use for stylometric identification
@@
 
-One configured, the call to the getAnonymouthInfoJSON input will
-overwrite the "test.txt" file on disk that is configured in the provided problem
-set. This will ensure that changing the document in Etherpad forces an
-update to the test file and thus ensuring that the 'latest' document
-is always anonymized. Once the problem set has been updated, the
-'Anonymouth library' is invoked. The 'Anonymouth library' is a forked
-version of the current Anonymouth application, which is designed to be
-used behind a Swing/AWT rich client GUI. A number of implementation
-challenges were present when trying to separate the core anonymization
-logic of Anonymouth from its GUI implementation - most specifically,
-although an 'engine' namespace exists which holds much of the
-anonymization logic, significant dependencies still existed between
-the 'engine' and the 'GUI' namespaces, specifically in the event
-handlers associated with the Editor screen and the GUIMain classes. Much of the work in this
-project consisted of reducing the coupling between these two
-namespaces.
+One configured, the call to the \texttt{getAnonymouthInfoJSON} input
+will overwrite the "test.txt" file on disk that is configured in the
+provided problem set. This will ensure that changing the document in
+Etherpad forces an update to the test file and thus ensuring that the
+'latest' document is always anonymized. Once the problem set has been
+updated, the 'Anonymouth library' is invoked. The 'Anonymouth library'
+is a forked version of the current Anonymouth application, which is
+designed to be used behind a Swing/AWT rich client GUI. A number of
+implementation challenges were present when trying to separate the
+core anonymization logic of Anonymouth from its GUI implementation -
+most specifically, although an 'engine' namespace exists which holds
+much of the anonymization logic, significant dependencies still
+existed between the 'engine' and the 'GUI' namespaces, specifically in
+the event handlers associated with the Editor screen and the
+\texttt{GUIMain} classes. Much of the work in this project consisted
+of reducing the coupling between these two namespaces.
 
 As much of the configuration logic was handled at the GUI layer (via
-ThePresident and GUIMain classes) we took the approach of refactoring
-the GUI layer to work in a 'headless' mode, that is, without any
-windows launching. Long-term it would be preferable to have no
-dependencies on the GUI namespace at all for the Stylometry Service,
-however this could not be achieved in the available timeframe for this
-project. The web service thus invokes a modified version of the
-ThePresident class, which coordinates reading configuration files,
-loading the configured problem set, and using numerous libraries
-(JGAAP and Weka among them) to conduct an adversarial stylometric
-analysis. The results are returned by the web service in the form of a
-JSON-encoded list of words to remove, as well as an indication of
-'changes needed' to the current text to reach an acceptable level of
-anonynmity.
+\texttt{ThePresident} and \texttt{GUIMain} classes) we took the
+approach of refactoring the GUI layer to work in a 'headless' mode,
+that is, without any windows launching. Long-term it would be
+preferable to have no dependencies on the GUI namespace at all for the
+Stylometry Service, however this could not be achieved in the
+available timeframe for this project. The web service thus invokes a
+modified version of the \texttt{ThePresident} class, which coordinates
+reading configuration files, loading the configured problem set, and
+using numerous libraries (JGAAP and Weka among them) to conduct an
+adversarial stylometric analysis. The results are returned by the web
+service in the form of a JSON-encoded list of words to remove, as well
+as an indication of 'changes needed' to the current text to reach an
+acceptable level of anonynmity.
 
@@
 The web application (bundled with all dependencies) can be downloaded
-by cloning https://github.com/LRParser/anonymouth and running the
-following command:
+as shown in Listing \ref{lst:download}.
 
+\begin{lstlisting}[caption={Download Web Application},label={lst:download}]
+git clone https://github.com/LRParser/anonymouth.git
 ./bootstrap.sh
+\end{lstlisting}
 
-This command will copy the latest JSAN JAR files to the 'lib'
+This command will copy the latest JSAN JAR files to the \texttt{lib}
 directory of the Play Framework Web Application, start a Play
-Framework Server on port 9000, and start an Etherpad Lite server on
-port 9001 over node.js.
+Framework Server on port $9000$, and start an Etherpad Lite server on
+port $9001$ over node.js.
 
@@
 
-Disadvantages to the web application include the fact that it offers fewer anonymization
-features (for instance, highlighting of specific text passages),
-instead focusing primarily on 'words to remove'. Furthermore, its
-security footprint is less well known, as it introduces a number of
-new dependencies / potential attack vectors such as JQuery, Twitter
-Bootstrap, Etherpad Lite, node.js, etc.
+Disadvantages to the web application include the fact that it offers
+fewer anonymization features (for instance, highlighting of specific
+text passages), instead focusing primarily on 'words to
+remove'. Furthermore, its security footprint is less well known, as it
+introduces a number of new dependencies / potential attack vectors
+such as JQuery, Twitter Bootstrap, Etherpad Lite, node.js, etc.
 
-For a user likely to be using
-mobile devices or a casual user looking to quickly anonymize texts,
-we suggest that the web interface may be a better option. For a user
-facing a highly sophisticated adversary and needing detailed
-anonymization suggestions, we suggest that the stand-alone application
-may be a better option. We note that there is no technical reason that
-could keep the web application from offering all of the same
-anonymization suggestions as the standalone application, and thus is
-may be the case that in the future the web application could be
-recommendable to a wider range of users.
+For a user likely to be using mobile devices or a casual user looking
+to quickly anonymize texts, we suggest that the web interface may be a
+better option. For a user facing a highly sophisticated adversary and
+needing detailed anonymization suggestions, we suggest that the
+stand-alone application may be a better option. We note that there is
+no technical reason that could keep the web application from offering
+all of the same anonymization suggestions as the standalone
+application, and thus is may be the case that in the future the web
+application could be recommendable to a wider range of users.
 standalone client
@@
 
-The web application can be deployed via the following commands on a
-Ubuntu 12.04 desktop installation:
+The web application can be deployed on a Ubuntu 12.04 desktop
+installation per Listings \ref{lst:install} and \ref{lst:start}.
 
@@
 reviewing the submissions from Mechanical Turk. For one sample paper,
-d 09.txt from the Brennan-Greenstadt corpus (Michael Brennan and Rachel Greenstadt.
-Practical Attacks Against Authorship Recognition Techniques in Proceedings of the Twenty-First Conference on Innovative Applications of Artificial Intelligence (IAAI), Pasadena, California, July 2009.
-), we noted that Anonymouth returned a "changes needed" score
-on the original document of 2.518, 2.677 for the users 'naive' attempt
-to anonymize over Mechanical Turk, and 2.467 for the attempt of one of
-the authors to anonymize using the web application created in this
-paper. Each of the two anonymization attempts for the 500-word
-document took approximately 15 minutes. Although these results are far from achieving statistical
-significance, they do suggest that it may be possible to use this
-software to achieve anonymization levels which surpass those of a
-'naive' anonymization attempt.
+d \texttt{09.txt} from the Brennan-Greenstadt corpus \cite{BrennanG09}
+, we noted that Anonymouth returned a "changes needed"
+score on the original document of $2.518$, $2.677$ for the users 'naive'
+attempt to anonymize over Mechanical Turk, and $2.467$ for the attempt
+of one of the authors to anonymize using the web application created
+in this paper. Each of the two anonymization attempts for the 500-word
+document took approximately 15 minutes. Although these results are far
+from achieving statistical significance, they do suggest that it may
+be possible to use this software to achieve anonymization levels which
+surpass those of a 'naive' anonymization attempt.
 
@@
 second used to update the client UI, on a 3.3 Ghz Core i5 Ubuntu 12.04
-Desktop machine, using 1 calculation thread for Anonymouth. These results suggests that any attempts at
-performance optimization should center around optimizing the
-performance of the Anonymouth configuration.
+Desktop machine, using 1 calculation thread for Anonymouth. These
+results suggests that any attempts at performance optimization should
+center around optimizing the performance of the Anonymouth
+configuration.
 
@@
 
-Further performance testing and optimization is required in order to support a true
-multi-user service. The authors would suggest using a web service
-based load test framework, such as Apache's JMeter or LoadUI, in order
-to fully test the service under various potential user loads.
+Further performance testing and optimization is required in order to
+support a true multi-user service. The authors would suggest using a
+web service based load test framework, such as Apache's JMeter or
+LoadUI, in order to fully test the service under various potential
+user loads.
 

### 2013-12-12 paper/paper.tex
one last look.

@@
 to passive sniffing.  A privacy web service must take great care to
-ensure that service does not compromise its user's privacy.  In
-Section \ref{sec:design} we provide our architecture and analysis the
-security and privacy.
+ensure that service does not compromise its user's privacy.
 
-\section{Design}
+\subsection{Novelty}
+
+Our novel contribution is the proposal of a stylometric web service
+and identifying the features of such a service.  We have provided a
+prototype implementation and identified areas of additional
+improvement.  Lastly, we suggest combining research from Game
+Artificial Intelligence to improve the usability and effectiveness of
+stylometric techniques.
+
+\subsection{Outline}
+In Section \ref{sec:design} we provide our architecture and analysis the
+security and privacy.  We provide several architectural and security
+features that a stylometric web service must and should have.  Section
+\ref{sec:security} provides a security analysis of the system design.
+A privacy analysis is provided in Section \ref{sec:privacy}.  The
+current state of the implementation is discussed in Section
+\ref{sec:impl} which includes details on how to reproduce our
+results.  Evaluation of the implementation and current architecture is
+provided in Section \ref{sec:evaluation}.
+
+\section{Design}\label{sec:design}
 
@@
 
-The architecture of Anonymouth is that of a conventional desktop
-application.  It uses a layered architecture with essentially two main
-components: the frontend Graphical User Interface (GUI) and the
-backend, consisting of the Weka machine learning toolkit and Jstylo.
-Jystlo is PSAL's stylometric analysis software.   Since Anonymouth was
-designed as a monolithic application, there are direct dependencies
-between the layers without the use of an adaptation layer.  Figure
-\ref{fig:jsan} illustrates the architecture in a layered drawing.  In
-this drawing, components, represented as boxes, can call software
-below and to the right.
+The architecture of the current adversarial stylometric software,
+Anonymouth, is that of a conventional desktop application.  It uses a
+layered architecture with essentially two main components: the
+frontend Graphical User Interface (GUI) and the backend, consisting of
+the Weka machine learning toolkit and JStylo.  JStylo is PSAL's
+stylometric analysis software.  Since Anonymouth was designed as a
+monolithic application, there are direct dependencies between the
+layers without the use of an adaptation layer.  Figure \ref{fig:jsan}
+illustrates the architecture in a layered drawing.  In this drawing,
+components, represented as boxes, can call software below and to the
+right.
 
 This design is sufficient for Anonymouth in its current form.  As a
-desktop appliccation, the user can anonymize her and the document
+desktop application, the user can anonymize her and the document
 locally without any additional attack vectors.
@@
 
-\subsection{Requirements for Web Service}
+\subsection{Requirements for Web Service}\label{sec:reqs}
 
@@
 migrating from a desktop to web service since the desktop application
-does not use any networked communicaiton.  However, there is little
+does not use any networked communication.  However, there is little
 benefit to using Anonymouth on the web if it compromises one's
 privacy.
-
-\subsubsection{Low-latency.}
-The web service as implemented is near-real-time, i.e. low-latency,
-bounded primarily be the performance of Anonymouth. One key feature of
-the current implementation is the asynchronous processing of
-stylometric information, which allows a user to continually modify a
-text while anonymity information is calculated in the background. The
-latency of the response times for each stylometric analysis is on the
-order of 1 to 2 minutes in the default configuration (see Performance
-section for futher details).
-
-A high latency system would not be well suited for a web service.  An
-example high latency system could simply entail sending an encrypted
-email to a third party who uses Anonymouth locally and returns the
-encrypted result.  While this high-latency system seems trivial, note
-that a naive implementation will reduce the user's privacy.  For
-example, email is very subject to traffic analysis
-\cite{Mathewson04practicaltraffic} and encrypted email is easy to
-detect, therefore this act alone would raise suspiction.  If
-this third party was offering a high-latency anonymiziation service
-for numerous people, the network graph would be easy to detect.
 
@@
 
-Availability is the measure of the measure of the accesibility and
-realibility of the system, e.g. how well does it handle errors.
+Availability is the measure of the measure of the accessibility and
+reliability of the system, e.g. how well does it handle errors.
 Interoperability refers to the degree with which a system can interact
@@
 review of a system's ability to protect sensitive data and prevent
-unautorized and undesired behaviour.  Testability is an important
+unauthorized and undesired behavior.  Testability is an important
 factor not only in development but also in a deployed system to ensure
@@
 refers to the interaction design.  Lastly, by privacy we mean how well
-a user's anonymitity is protected.
+a user's anonymity is protected.
 
@@
 
-There are many implemenation details to achieve availability that are
+There are many implementation details to achieve availability that are
 beyond the scope of this paper.  We attest that a stylometric service
@@
 web architecture.  Specifically, it should be a service based on
-Representational State Transfer (REST)\cite{Fielding2000}.  REST web
+Representational State Transfer (REST) \cite{Fielding2000}.  REST web
 services define a framework that is client-server, has a uniform
@@
 service.  Using a REST service, the client software can be a web
-browser, which is nearly ubiqiteious on mobile devices.
+browser, which is nearly ubiquitous on mobile devices.
 
@@
 One of the goals of the service is provide a platform for stylometric
-research.  In this sense in must be modifable to accomodate different
+research.  In this sense in must be modifiable to accommodate different
 kinds of experiments including ones not currently anticipated.
-Software engineering best pratices are applicable here mainly having
+Software engineering best practices are applicable here mainly having
 well abstracted interfaces and modular components.  As a RESTful web
@@
 
+However, we do specify that the service should be low-latency.  The
+web service as implemented is near-real-time, i.e. low-latency,
+bounded primarily be the performance of Anonymouth. One key feature of
+the current implementation is the asynchronous processing of
+stylometric information, which allows a user to continually modify a
+text while anonymity information is calculated in the background. The
+latency of the response times for each stylometric analysis is on the
+order of 1 to 2 minutes in the default configuration.
+
+A high latency system would not be well suited for a web service.  An
+example high latency system could simply entail sending an encrypted
+email to a third party who uses Anonymouth locally and returns the
+encrypted result.  While this high-latency system seems trivial, note
+that a naive implementation will reduce the user's privacy.  For
+example, email is very subject to traffic analysis
+\cite{Mathewson04practicaltraffic} and encrypted email is easy to
+detect, therefore this act alone would raise suspicion.  If
+this third party was offering a high-latency anonymization service
+for numerous people, the network graph would be easy to detect.
+
 \subsubsection{Security.}
@@
 the user's data.  The user is trusting the service with their corpus
-and document to anonymize and that must be revealed to unauthroized
+and document to anonymize and that must be revealed to unauthorized
 users.  However, one of the goals of this service is to allow multiple
 authors to collaborate.  In this case, the confidentiality
-requirements are more interesting.  We don't specifiy an
+requirements are more interesting.  We do not specify an
 implementation, but there are various techniques that could satisfy
@@
 
+Usability is often sacrificed for security in privacy and security
+software.  Of course, the most secure system is the one that does not
+communicate with any other entity.  The target audience for
+stylometric software are authors, of varying technical capacity.
+Recently, organizations like the Freedom of the Press Foundation
+\cite{pressfreedom} have shown increasing interest in educating
+journalists on cryptographic and privacy enhancing software.  While
+usability is difficult to quantify, the service must be usable by
+non-technical end users without a detailed knowledge in stylometry.
+
 \subsubsection{Privacy.}
 
+The service must protect the privacy of its users.  Specifically, it
+must not leak the corpus nor the target document.  It also must be
+vulnerable to traffic analysis, as that could possibly lead to linkage
+attacks.  Especially because the documents could contain references to
+other accounts or activity that would make them prime for attacks as
+discussed in \cite{Narayanan:2008:RDL:1397759.1398064}.
+
+The privacy of the service should also be maintained.  A critical
+difference between a web service and a standalone application is that
+the software on a web service runs on third-party hardware.  While
+perhaps obvious, this as fundamental trust issues.  Therefore, the
+knowledge that a stylometric service is running in a certain
+geographical area, or more specifically, on a specific Internet
+Service Provider, could make it vulnerable to attacks.
+
+Furthermore, it is assumed that the host of the service is trusted.
+This is a significant assumption since users of most ``Cloud''
+providers rent time on the hardware.  Worse, they are not the sole
+users of said hardware and their application is shared with other
+users.  The choice of a service provider is outside the scope of this
+document, but this consideration should not be made lightly when
+choosing where to deploy the service.
+
+The service must not engage in browser fingerprinting
+\cite{Eckersley:2010:UYW:1881151.1881152}.  If deployed behind a Tor
+Hidden service, browsers should be nearly indistinguishable when
+everybody is using the Tor Browser Bundle.  Debug information must be
+kept to a minimum as well.  This service must use the ``Privacy by
+Architecture'' approach \cite{Spiekermann_Cranor:2009} and ensure that
+debug information and collection is kept to a minimum.  Debug
+information is particularly sensitive since to re-create a bug, one
+may need the target document.  However, under no circumstances should
+the user's document be released to developers as that would compromise
+the confidentiality of the document.  Plus, this extends opportunities
+for attack vectors through debug channels.
+
 \subsection{Example Architecture}
+
+Figure \ref{fig:jsanaas} illustrates an example architecture with
+qualities from Section \ref{sec:reqs}.  The main entry point is a
+lightweight dispatcher that sits behind a Tor Hidden Service.  The
+user only need to know this address and can connect to the service
+through Tor.
+
+The backend has several modular endpoints.  The first of which is a
+directory service.  The directory service accepts registration from
+other services and provides the location of the service when
+queried.  This feature help to provide availability and testability.
+Especially as a research platform, additional services or endpoints
+may need to be added to the system.  A registration service tracks the
+dynamic installation of such services and when all services in the
+system check with the registration service, they can quickly use the
+new addition.
 
@@
 \end{figure*}
-\section{Security Analysis}
+
+Notice that each feature is split into its endpoint.  This also helps
+with the modularity and availability.  Backup endpoints can be
+registered with the registration service and all endpoints frequently
+queried, or they can provide notifications, such that services
+maintain their uptime.  This modularity also helps with moving the
+location of the service.  As long as the lightweight front-end remains
+known, all backend services can move without the knowledge of the
+user.  Perhaps each individual backend service would be its own Tor
+Hidden Service.  The onion addresses would only to be known to the
+Registration Service.  However, as each Hidden Service connection is
+six hops through Tor, the performance impact would have to be more
+closely studied.
+
+\section{Security Analysis}\label{sec:security}
 
@@
 
-Although web accessbility may be a significant risk from a usability
+Although web accessibility may be a significant risk from a usability
 standpoint, the anecdotal infrequency with which adversarial
@@
 where the user believes she is communicating with a specific
-Stylometry Service, but is infact communicating via an impersonated
+Stylometry Service, but is in fact communicating via an impersonated
 target.
 
-{\bf Replay attacks}: An evesdropper may replay a message to the
-webservice in an attempt to surrepituously revert parts of the text to
+{\bf Replay attacks}: An eavesdropper may replay a message to the
+web service in an attempt to surreptitiously revert parts of the text to
 earlier versions. This may be possible as it is not documented whether
@@
 used by to detect differences in link coloring across frames (allowing
-an adversary to determine if a particular styometry service has been
+an adversary to determine if a particular stylometry service has been
 visited, for instance).
 
-Note: We do not know if any of these vectors allows for a specific
+We do not know if any of these vectors allows for a specific
 attack, but suggest they should be considered for any future
@@
 
-\section{Privacy and Anonymity Analysis}
+Lastly, this application uses numerous third party libraries and
+technologies.  The added complexity from each additional library or
+toolkit, exposes the service to additional vulnerabilities.  It also
+makes the software more difficult to audit by third parties.
+Deploying a Stylometric service required numerous frameworks, some of
+which are in very rapid development.
+
+\section{Privacy and Anonymity Analysis}\label{sec:privacy}
 
@@
 to ensure that the IP of the client cannot be directly linked to the
-IP of the service.
+IP of the service.  The Tor Hidden Service also provides protection of
+the location of the service.
 
-\section{Implementation Details}
+A current weakness of this system is that the service is considered a
+trusted third party.  If the service is compromised, the documents can
+be extracted and the author revealed.  We considered other
+architectures, for example, one that delivered a more feature full
+application to the browser, however this would be more like a content
+delivery system.
+
+Additionally, by multi-author implementation exposes the target
+document to another user.  Therefore, the circle of trust is extended
+from the service to the other party.  There is also no authentication
+of the other party.  The service should provide an OTR like mechanism
+for inviting the other party into the editing session and verifying
+the authenticity of the user.
+
+\section{Implementation Details}\label{sec:impl}
 
@@
 used here) in turn has major dependencies on node.js for building and
-running the backend service.
+running the backend service.  Figure \ref{fig:text_endpoint} shows an
+example screenshot of the stylometric only endpoint.
+
+\begin{figure}
+  \centering
+    \includegraphics[width=0.4\textwidth]{img/text_endpoint.png}
+  \caption{Screenshot of the text endpoint}
+  \label{fig:text_endpoint}
+\end{figure}
 
@@
 control and instructions for the user to enter in the document they
-wish to anonymize. The etherpad control is implemented as an iframe
+wish to anonymize. The Etherpad control is implemented as an iframe
 which serves an Etherpad that is connected to the node.js server
@@
 
-The web service as implemented currently supports only 1 author as the
-assumption is made that the author has pre-configured the "doc set"
-(also referred to as 'problem set' in Anonymouth source) that provides
+Figure \ref{fig:impl} shows the current implemented service in a
+layered architecture.  There are currently two endpoints that run in
+the Play Framework: a pure stylometric endpoint and the adversarial
+endpoint.  The adversarial endpoint is Anonymouth and also contains
+Etherpad, the collaborative editor.  Currently, the endpoints are both
+meant to run on the same server.
+
+\begin{figure}
+  \centering
+    \includegraphics[width=0.2\textwidth]{img/impl.pdf}
+  \caption{Current implementation of JSANaaS as a layered drawing}
+  \label{fig:impl}
+\end{figure}
+
+The web service as implemented currently supports only one author as the
+assumption is made that the author has pre-configured the document set
+(also referred to as \emph{problem set} in Anonymouth source code) that provides
 references as to the author's own writing style, as well as writing
@@
 styles that are different than that of the active author. The user can
-additionally configure the anonymouth properties file
-(\texttt{anonymouthprop.prop}) in the jsan resources directory to influence
+additionally configure the Anonymouth properties file
+(\texttt{anonymouthprop.prop}) in the JSAN resources directory to influence
 settings such as the feature set to use for stylometric identification
@@
 One configured, the call to the \texttt{getAnonymouthInfoJSON} input
-will overwrite the "test.txt" file on disk that is configured in the
-provided problem set. This will ensure that changing the document in
-Etherpad forces an update to the test file and thus ensuring that the
-'latest' document is always anonymized. Once the problem set has been
-updated, the 'Anonymouth library' is invoked. The 'Anonymouth library'
-is a forked version of the current Anonymouth application, which is
-designed to be used behind a Swing/AWT rich client GUI. A number of
-implementation challenges were present when trying to separate the
-core anonymization logic of Anonymouth from its GUI implementation -
-most specifically, although an 'engine' namespace exists which holds
-much of the anonymization logic, significant dependencies still
-existed between the 'engine' and the 'GUI' namespaces, specifically in
-the event handlers associated with the Editor screen and the
-\texttt{GUIMain} classes. Much of the work in this project consisted
-of reducing the coupling between these two namespaces.
+will overwrite the \texttt{test.txt} file on disk that is configured
+in the provided problem set. This will ensure that changing the
+document in Etherpad forces an update to the test file and thus
+ensuring that the 'latest' document is always anonymized. Once the
+problem set has been updated, the Anonymouth library is invoked. The
+Anonymouth library is a forked version of the current Anonymouth
+application, which is designed to be used behind a Swing/AWT rich
+client GUI. A number of implementation challenges were present when
+trying to separate the core anonymization logic of Anonymouth from its
+GUI implementation - most specifically, although an engine namespace
+exists which holds much of the anonymization logic, significant
+dependencies still existed between the engine and the GUI
+namespaces, specifically in the event handlers associated with the
+Editor screen and the \texttt{GUIMain} classes. Much of the work in
+this project consisted of reducing the coupling between these two
+namespaces.
 
@@
 Stylometry Service, however this could not be achieved in the
-available timeframe for this project. The web service thus invokes a
+available time frame for this project. The web service thus invokes a
 modified version of the \texttt{ThePresident} class, which coordinates
@@
 as an indication of 'changes needed' to the current text to reach an
-acceptable level of anonynmity.
+acceptable level of anonymity.
 
@@
 
-\section{Comparison to Stand-alone Application}
-
-The stand-alone application has both advantages and disadvantages
-relative to the web service. To start with advantages: it contains
-more robust error handling, offers a GUI to create a problem set, and
-provides a richer editing experience for anonymized
-texts. Disadvantages concern ease of use (users must download and
-execute a JAR file) and supported platforms (it is unlikely that this
-JAR file will be supported on many mobile phones, for instance). The
-Stylometry Service, in contrast, is potentially more accessible than
-the standalone application: it can be accessed via mobile phones and
-tablets, for instance. Likewise application delivery may be simpler -
-nothing must be downloaded locally. Furthermore, the web application
-maintains a 'timeline' of changes made to a text and also allows for
-simple multi-party anonymization of documents.
-
-Disadvantages to the web application include the fact that it offers
-fewer anonymization features (for instance, highlighting of specific
-text passages), instead focusing primarily on 'words to
-remove'. Furthermore, its security footprint is less well known, as it
-introduces a number of new dependencies / potential attack vectors
-such as JQuery, Twitter Bootstrap, Etherpad Lite, node.js, etc.
-
-For a user likely to be using mobile devices or a casual user looking
-to quickly anonymize texts, we suggest that the web interface may be a
-better option. For a user facing a highly sophisticated adversary and
-needing detailed anonymization suggestions, we suggest that the
-stand-alone application may be a better option. We note that there is
-no technical reason that could keep the web application from offering
-all of the same anonymization suggestions as the standalone
-application, and thus is may be the case that in the future the web
-application could be recommendable to a wider range of users.
-standalone client
-
-\section{Deployment}
+\subsection{Deployment}
 
@@
 
-\section{Single User Evaluation}
+\subsection{Comparison to Stand-alone Application}
+
+The stand-alone application has both advantages and disadvantages
+relative to the web service. To start with advantages: it contains
+more robust error handling, offers a GUI to create a problem set, and
+provides a richer editing experience for anonymized
+texts. Disadvantages concern ease of use (users must download and
+execute a JAR file) and supported platforms (it is unlikely that this
+JAR file will be supported on many mobile phones, for instance). The
+Stylometry Service, shown in Figure \ref{fig:text_endpoint}, in
+contrast, is potentially more accessible than the standalone
+application: it can be accessed via mobile phones and tablets, for
+instance. Likewise application delivery may be simpler - nothing must
+be downloaded locally. Furthermore, the web application maintains a
+time line of changes made to a text and also allows for simple
+multi-party anonymization of documents.
+
+Disadvantages to the web application include the fact that it offers
+fewer anonymization features (for instance, highlighting of specific
+text passages), instead focusing primarily on ``words to
+remove''. Furthermore, its security footprint is less well known, as it
+introduces a number of new dependencies / potential attack vectors
+such as JQuery, Twitter Bootstrap, Etherpad Lite, node.js, etc.
+
+For a user likely to be using mobile devices or a casual user looking
+to quickly anonymize texts, we suggest that the web interface may be a
+better option. For a user facing a highly sophisticated adversary and
+needing detailed anonymization suggestions, we suggest that the
+stand-alone application may be a better option. We note that there is
+no technical reason that could keep the web application from offering
+all of the same anonymization suggestions as the standalone
+application, and thus is may be the case that in the future the web
+application could be recommendable to a wider range of users.
+standalone client
+
+\section{Evaluation}\label{sec:evaluation}
+
+We conducted two evaluations of the service.  The first was a
+single-user evaluation that focused on the stylometric capabilities.
+The second was a multi-user evaluation.  In this evaluation, the focus
+was on the experience and usability of a multi-user stylometric
+interaction.
+
+\subsection{Single User Evaluation}
 
@@
 
-\section{Multiple Concurrent User Evaluation}
+\subsection{Multiple Concurrent User Evaluation}
 
-TODO
+A simple multi-user evaluation was conducted.  The noticeable feature
+in the multi-user scenario was the real-time collaboration.  An example
+screen shot in Figure \ref{fig:multi}.  When an experienced user
+interacted with a novice user, the learning curve of the novice user
+was drastically reduced.  The multi-user platform also allows users to
+divide and conquer the work, which allowed for quicker anonymization
+of the document.
 
-\section{Evaluation of Architecture Qualities}
+\begin{figure}
+  \centering
+    \includegraphics[width=0.5\textwidth]{img/mult_user.png}
+  \caption{Multi-user screenshot}
+  \label{fig:multi}
+\end{figure}
 
-\subsection{Performance.}
+In this multi-user test, both authors were human.  However, we would
+like to see the multi-user as an Artificial Intelligence (AI) Agent.
+The agent, acting as a author, could help the primary author anonymize
+the target document.  We believe that this application is well-suited
+for an AI because of a clear objective function: the changes-needed
+score.  A naive approach could simply apply adversarial search with
+pruning, like Mini-max to analyze the document and replace each
+suggested word with a thesaurus lookup.
+
+A more thorough approach is to incorporate a Drama Manager agent as
+found in video games \cite{10.1109/WI-IAT.2009.143},
+\cite{conf/aaaiss/SullivanCM09}, \cite{Magerko04aicharacters}.  In
+these games, a Drama Manager (DM) acts as a benevolent AI to manage the
+player's experience.  The DM monitors various features of the game and
+can change elements in game.  If the game is too challenging, the DM
+can scale the difficulty by offering additional power-ups, or if it is
+too easy, the DM will introduce more adversaries.
+
+The application to this service is that the AI can monitor the user's
+interaction on the site.  If the user is slow to start using the
+software, the agent can offer helpful tips.  However, an experienced
+user will immediately start using the service and would not need these
+tips.  Similarly, if the user is not replacing words in a direction
+that improves the document, the agent, acting as a second author, can
+offer assistance.
+
+\subsection{Evaluation of Architecture Qualities}
+
+In the following sections, we analyze each architecture against the
+design criteria in Section \ref{sec:design}.  We evaluate our
+implementation as of the time of this writing and identify areas that
+need further work.
+
+\subsubsection{Availability.}
+
+As implemented the service runs on one host and none of the redundancy
+or resiliency features have been added.  This may be acceptable for a
+prototype, but for the service to act as a research platform, more
+work must be done to ensure that it is reliable.  We did not perform
+any hardening or enhance the protection of the web service through the
+operating system in any way.  Each of those efforts would certainly
+help maintain the availability goal.
+
+\subsubsection{Interoperability}
+
+We have tested the current software with popular web browsers and each
+of them have been able to interact with the site.  The heavy lifting
+of this interoperability is the Play Framework, which allows for rapid
+development of a RESTful web service.  Even though the client software
+need only a browser, there is great variety in browsers.  Again,
+restricting the browser to the Tor Browser Bundle would significantly
+help otherwise various browsers could have unique interoperability issues.
+
+\subsubsection{Modifiability}
+
+We did not implement the registration service, therefore the service
+is not as modifiable as we would like.  The main purpose of this
+effort was to evaluate the feasibility and during the development we
+could rapidly push changes to the server.  The Play Framework assists
+greatly in this effort, but inherently, web service development can
+lead to quicker deployments than traditional applications.
+
+\subsubsection{Performance.}
 
@@
 required for the Anonymouth analysis, with less than 1 additional
-second used to update the client UI, on a 3.3 Ghz Core i5 Ubuntu 12.04
+second used to update the client UI, on a 3.3 GHz Core i5 Ubuntu 12.04
 Desktop machine, using 1 calculation thread for Anonymouth. These
@@
 After each stylometric analysis is complete, the web service ensures
-all relevant anonymouth resources are closed. This allows the web
+all relevant Anonymouth resources are closed. This allows the web
 service to be used over a long period of time (20 or more
@@
 
-\subsection{Testability.}
+\subsubsection{Testability.}
 
@@
 
+\subsubsection{Security and Privacy}
+
+Security and Privacy findings were analyzed in Sections
+\ref{sec:security} and \ref{sec:privacy}.
+
+\subsubsection{Usability}
+
+We feel that the interaction with the interface is improved as web
+service.  The web service provides a very common experience for the
+user through her browser with limited options.  The software is a
+prototype and overall, the interface is intuitive and similar to other
+web applications.  The addition of the Etherpad enables a very easy
+collaborative editing platform and the suggested words and very
+clearly identified.
+
 \section{Conclusion}
@@
 web interface may offer usability advantages while still providing a
-meaningful increase in author anonymity.  The second contribution is that this is
-the first framework for multi-author adversarial stylometry.  Our
-results here suggest TODO.
+meaningful increase in author anonymity.
+
+The second contribution is that this is the first framework for
+multi-author adversarial stylometry.  Our results here suggest
+multi-author collaboration and improve the usability of the software
+through real-time mentoring.  Also, the addition of an AI agent could
+replace the human mentor and provide a more consistent experience.
+
+While the software is a prototype, we believe that a stylometric web
+service is feasible.  There are challenges to overcome, such as the
+trusted service provider, but we feel that these are solvable.
 
@@
 
-\begin{table}
-  \centering
-  \begin{tabular}{l | c}
-    Milestone & Date\\
-    \hline
-
-    Document initial design & October 28\\
-    Finish porting JSAN to a web service & November 4\\
-    Add the Firebase editro & November 11\\
-    Add the third party feature & November 18\\
-    Conduct evaluation & November 25\\
-    Provide Paper and Presentation & December 2
-
-  \end{tabular}
-  \caption{Project Milestones}
-  \label{tab:milestones}
-\end{table}
-
 \subsection*{Future Work}
 
-The scope of this project is designed to completed in one Drexel
-quarter, however we have several ideas for continued work.  With a web
-service, we can offer real-time adversarial stylometry.  Assume Alice,
-who has a blog, wants to anonymize her next blog post.  She would
-connect to our web service, submit the URL for her blog and then write
-her next post with adversarial stylometry.  This real-time data
-crawling at this scale is simply not feasible with stand alone
-software.
+With a web service, we can offer real-time adversarial stylometry.
+Assume Alice, who has a blog, wants to anonymize her next blog post.
+She would connect to our web service, submit the URL for her blog and
+then write her next post with adversarial stylometry.  This real-time
+data crawling at this scale is simply not feasible with stand alone
+software.  Currently the corpus must be selected before deployment of
+the service, but building a corpus on the fly would be interesting.
+However, there are challenges since the  data is especially raw.
+For example, the author may have signed her name to the blog post or
+left in other details that could threaten her anonymity.
 
-Now that a third party will be re-writing documents, we feel that it
+A third party could re-write the document entirely.  In this case, it
 is important to obfuscate the content from the re-writer.  One idea,
@@
 native style.  The combined document, would contain $n$ author styles,
-where $n$ is the number of re-writing authors.
+where $n$ is the number of re-writing authors.  The concern lies with
+storing the document and making it available to re-writers.  We
+eliminated this complication by focusing on real-time anonymization in
+a low-latency environment.  The third party re-writer could also be
+achieved by an AI agent, which could eliminate this issue.
+
+Additional testing should be conducted on mobile devices.  The tests
+on these devices would mainly be usability studies to ensure that the
+service can be effectively used on computationally limited devices.
+The ideal platform would be an Android based tablet or smart phone,
+since there are Tor clients that can be easily installed on these
+devices.  The extra challenge here is uploading documents and entering
+text as the lack of keyboard may make this a bit more complicated.
+However, these are implementation details that can be overcome.
 
